<<<<<<< HEAD
---
title: "Reduce ssf-data"
author: "anneMehl"
date: "5 april 2018"
output:
  word_document: default
  pdf_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##### load data from Christers gardermoen analysis
```{r}
 load("processdata/gpsdata2.rda")

```

  
##### split data on "strat" with function "split" to get a list as long as "strat"
```{r}
  dvvvsplit <- split(gpsdata2, f = as.factor(gpsdata2$strat))
```
  
  
##### half the size of the data 
```{r}
  dvvvsample <- sample(dvvvsplit, 155767)
```
  
  
##### half the amount of random steps, by keeping only the last 5 rows (tail) of ech list element 
```{r}
  dvvv <- lapply(dvvvsample, tail, 5)
  save(dvvv, file="dvvv.rda")
  load("output/dvvv.rda")
```
For some reason (probably because this list is super large) the upper chunk is not processing well.
  
##### convert the list back into a datframe to use it in the ssf model
```{r}
    dvvv1 <- do.call(rbind, dvvv)
    save(dvvv1, file="dvvv1.rda")
    load("output/dvvv1.rda")
```




=======
---
title: "Reduce ssf-data"
author: "anneMehl"
date: "5 april 2018"
output:
  word_document: default
  pdf_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##### load data from Christers gardermoen analysis
```{r}
 load("processdata/gpsdata2.rda")

```

  
##### split data on "strat" with function "split" to get a list as long as "strat"
```{r}
  dvvvsplit <- split(gpsdata2, f = as.factor(gpsdata2$strat))
```
  
  
##### half the size of the data 
```{r}
  dvvvsample <- sample(dvvvsplit, 155767)
```
  
  
##### half the amount of random steps, by keeping only the last 5 rows (tail) of ech list element 
```{r}
  dvvv <- lapply(dvvvsample, tail, 5)
  save(dvvv, file="dvvv.rda")
  load("output/dvvv.rda")
```
For some reason (probably because this list is super large) the upper chunk is not processing well.
  
##### convert the list back into a datframe to use it in the ssf model
```{r}
    dvvv1 <- do.call(rbind, dvvv)
    save(dvvv1, file="dvvv1.rda")
    load("output/dvvv1.rda")
```




>>>>>>> 33073c58e577f151a44cf063f78edd1b3c2e3689
