<<<<<<< HEAD
---
title: "SSF: survival package vs. ResourceSeceltion package"
author: "anneMehl"
date: "9 april 2018"
output: word_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



### Old way, using library survival

```{r}
  load("output/dvvv1.rda")

  starttime <- Sys.time()
  mod1_dvvv2 <- coxph(Surv(rep(1, length(use)), use) ~ strata(strat) + pspline(step_length,2) +
                  prop_ar5_agri + prop_ar5_bog + prop_ar5_urban + prop_young_forest + prop_water + slope +
                  prop_airport + crossed_rail + road_cross + fence_cross + dist_passage + log_road_dist + log_road_traffic + road_type_notA + log_road_dist:log_road_traffic + log_road_dist:road_type_notA, data = dvvv2)
  endtime <- Sys.time()
  endtime-starttime
  save(mod1_dvvv2, file="mod1_dvvv2.rda")
  
  # save(mod1, file="mod1.rda")
  load("output/mod1.rda")
  load("output/mod1_dvvv2")
  
  summary(mod1)
  summary(mod1_dvvv2)
```



##### Run Christers coxph model to compare the coefficients  

```{r}
  load("processdata/gpsdata2.rda")

  starttime <- Sys.time()
  mod7chr <- coxph(Surv(rep(1, length(use)), use) ~ strata(strat) + pspline(step_length,2) + 
                  prop_ar5_agri + prop_ar5_bog + prop_ar5_urban + prop_young_forest + prop_water + slope + 
                  prop_airport + crossed_rail + road_cross + fence_cross + dist_passage + log_road_dist + log_road_traffic + road_type_notA + log_road_dist:log_road_traffic + log_road_dist:road_type_notA, data = gpsdata2)
  endtime <- Sys.time()
  endtime-starttime
  # save(mod7chr, file = "mod7chr.rda")
  load("output/mod7chr.rda")
  summary(mod7chr)
```



##### Loading the ssf model run with rspf from the ResourceSeceltion package with 25 bootstraps
```{r}
load("output/mod2_25.rda")
mod2_25 <- mod2
load("processdata/models.rda")# loads mod_ssf and mod_sspf
load("output/mod1.rda")  
load("output/mod2.rda")
load("output/mod7chr.rda")
load("processdata/models2.rda") # loads mod_ssf, mod_sspf, mod_sspfv2, mod_sspfv3 
summary(mod_ssf)
summary(mod_sspf)
summary(mod_sspfV2) # probit link
summary(mod_sspfV3) # c log log link
summary(mod2_25)
```
  
  
##### Compare coefficeints of both (Christers and mine) coxph models AND the two run in ResourceSelection package
Put model estimates into temporary data.frames:

```{r}
  model1frame <- data.frame(Variable = rownames(summary(mod1)$coef),
                            Coefficient = summary(mod1)$coef[, 1],
                            SE = summary(mod1)$coef[, 2],
                            modelname = "mod1")
  
  model7frame <- data.frame(Variable = rownames(summary(mod7chr)$coef),
                            Coefficient = summary(mod7chr)$coef[, 1],
                            SE = summary(mod7chr)$coef[, 2],
                            modelname = "mod7")
  
  modelrspackage <- data.frame(Variable = rownames(summary(mod2)$coef),
                            Coefficient = summary(mod2)$coef[, 1],
                            SE = summary(mod2)$coef[, 2],
                            modelname = "rspackage")
  
  modelrspackage25 <- data.frame(Variable = rownames(summary(mod2_25)$coef),
                            Coefficient = summary(mod2_25)$coef[, 1],
                            SE = summary(mod2_25)$coef[, 2],
                            modelname = "ssfboot")
  
  
  model_ssf <- data.frame(Variable = rownames(summary(mod_ssf)$coef),
                            Coefficient = summary(mod_ssf)$coef[, 1],
                            SE = summary(mod_ssf)$coef[, 2],
                            modelname = "mod_ssf")
  
  model_sspf <- data.frame(Variable = rownames(summary(mod_sspf)$coef),
                            Coefficient = summary(mod_sspf)$coef[, 1],
                            SE = summary(mod_sspf)$coef[, 2],
                            modelname = "mod_sspf")
  
  model_sspfv2 <- data.frame(Variable = rownames(summary(mod_sspfV2)$coef),
                            Coefficient = summary(mod_sspfV2)$coef[, 1],
                            SE = summary(mod_sspfV2)$coef[, 2],
                            modelname = "mod_sspfV2")
  
  model_sspfv3<- data.frame(Variable = rownames(summary(mod_sspfV3)$coef),
                            Coefficient = summary(mod_sspfV3)$coef[, 1],
                            SE = summary(mod_sspfV3)$coef[, 2],
                            modelname = "mod_sspfV3")
  
  modelrspackage$SE <- "0"
  modelrspackage$SE <- as.numeric(modelrspackage$SE)
  model_sspf$SE <- "0"
  model_sspf$SE <- as.numeric( model_sspf$SE)
  model_sspfv2$SE <- "0"
  model_sspfv2$SE <- as.numeric( model_sspfv2$SE)
  model_sspfv3$SE <- "0"
  model_sspfv3$SE <- as.numeric( model_sspfv3$SE)
  
```


Then I combine these data.frames:
```{r}
  allmodelframe <- data.frame(rbind(modelrspackage, model_ssf, model_sspf, model_sspfv2, model_sspfv3))
```


Here, the width of the confidence intervals is being specified
```{r}
  interval1 <- -qnorm((1-0.95)/2)  # 90% multiplier
  interval2 <- -qnorm((1-0.95)/2)  # 95% multiplier
```


```{r figure-setup, echo = FALSE, include = FALSE}
knitr::opts_chunk$set(fig.path = "figs/", fig.width = 6.5,
                      fig.height = 4, fig.align = "center")
```


```{r comparing different ssf-models, fig.cap='Comparing different ssf-models'}
ggplot(allmodelframe, aes(colour = modelname)) + 
    geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) + 
    geom_linerange(aes(x = Variable, ymin = Coefficient - SE*interval1,
                                  ymax = Coefficient + SE*interval1),
                              lwd = 1, position = position_dodge(width = 1/2)) + 
    geom_pointrange(aes(x = Variable, y = Coefficient, ymin = Coefficient - SE*interval2,
                                   ymax = Coefficient + SE*interval2),
                               lwd = 1/2, position = position_dodge(width = 1/2),
                               shape = 21, fill = "WHITE") + coord_flip() + theme_bw() + 
    ggtitle("sspf: comparing different models")

```
  

##### Model selection with AIC
```{r}
AIC(mod2, mod_sspf, mod_sspfV2, mod_sspfV3)
```

  
#### New way, using library ResourceSelection
This bit has been run on Brams computer, because it takes very long
  
```{r}
  ## LOOK FOR STRATS WITH 0, IF IT RETURNS STH, RUN THE CODE BELOW
load("output/dvvv1.rda")
  which(tapply(dvvv1$use, dvvv1$strat, max)==0)
  
  dvvv2 <- dvvv1[!(dvvv1$strat %in% as.numeric(names(which(tapply(dvvv1$use, dvvv1$strat, max)==0)))),]
  which(tapply(dvvv2$use, dvvv2$strat, max)==0)
  head(dvvv2)
  nrow(dvvv2)
  nrow(dvvv1)
  # save(dvvv2, file="dvvv2.rda")
  
  load("output/dvvv2.rda")
  
  starttime <- Sys.time()
  mod2 <- rspf(use~ step_length + prop_ar5_agri + prop_ar5_bog + prop_ar5_urban + prop_young_forest + prop_water + slope + 
                 prop_airport + crossed_rail + road_cross + fence_cross + dist_passage + log_road_dist + log_road_traffic + 
                 road_type_notA + log_road_dist:log_road_traffic + log_road_dist:road_type_notA,
                   data=dvvv2, m=dvvv2$strat, B=0, link="logit")
  endtime <- Sys.time()
  endtime-starttime
  
  # save(mod2, file="mod2.rda")
  
  load("output/mod2.rda")
  str(mod2)
  summary(mod2)
  mep(mod2)
```



##### Plot the effects of the road variables for the ResourceSelection model
Firt we prepare a new data set to simulate or predict some things later in the plots. (?)

```{r}
load("output/mod2_25.rda")
load("output/mod2.rda")
mod2_25 <- mod2
load("output/dvvv2.rda")
tmp <- dvvv2
          newdat <- tmp[rep(1, 2000),] 
          newdat$road_dist <- c(c(0,0:498)*2, c(0,0:498)*2, c(0,0:498)*2, c(0,0:498)*2) #x axis (0=crossing, then from (0=no crossing) to 996 m in steps of 2 - the whole thing repeated 4 times
          newdat$log_road_dist <- log10(newdat$road_dist+1)  
          hist(dvvv2$road_traffic[dvvv2$road_traffic>0])
          quantile(dvvv2$road_traffic[dvvv2$road_traffic>0], 0.25)
          quantile(dvvv2$road_traffic[dvvv2$road_traffic>0], 0.95)
          newdat$road_traffic <- rep(c(0,0,1500,20000), each=500) # we don't predcit traffic in a continuous way - we use cross; no traffic, low, med and high traffic
          newdat$log_road_traffic <- log10(newdat$road_traffic+1)    
          newdat$road_cross <- 0
          newdat$road_cross[c(1,501, 1001, 1501)] <- 1
          newdat$road_cross <- as.factor(newdat$road_cross)
          newdat$road_type_notA <- 0
          newdat$road_type_notA[c(1:500)] <- 1
          newdat$road_type_notA <- as.factor(newdat$road_type_notA)
          
library("boot", lib.loc="~/R/win-library/3.4")
d <- newdat
m <- mod_sspf

#  I think that model.matrix will generate automatically the columns that you need, give it a try:

d <- na.omit(d)

X <- model.matrix(m$formula, data=d)
    
predvals <- (X %*% coef(m)[match(colnames(X), names(coef(m)))])[,1]
     
d$linpred <- predvals
d$predprob <- inv.logit(d$linpred)
head(d)

```



###### Version without log transforming distance to road:        
```{r}
#    xlab="log distance to road", ylab="step selection") 
# high traffic volume (20000) and no possibility for road crossing (0)
plot(newdat$road_dist[newdat$road_traffic==20000 & newdat$road_cross==0], d$predprob[newdat$road_traffic==20000 & newdat$road_cross==0], type="l", col="red", ylim=c(0,0.0002), xlim = c(),
xlab="Avstand til veg (meter)", ylab="Strekningsvalg", cex.lab=1.5, cex.axis=1.1, lty=1, lwd=2) #

lines(newdat$road_dist[newdat$road_traffic==1500 & newdat$road_cross==0], d$predprob[newdat$road_traffic==1500 & newdat$road_cross==0], type="l", col="blue", lty=1.5, lwd=2) #
#lines(newdat$log_road_dist[newdat$road_traffic==0 & newdat$road_cross==0 & newdat$road_type_notA==0], pred$fit[newdat$road_traffic==0 & newdat$road_cross==0 & newdat$road_type_notA==0], type="l", col="grey") # predictionif we really had zero traffic - wihc is quite impossible. Also, we predict outside the range - we get artefacts
lines(newdat$road_dist[newdat$road_traffic==0 & newdat$road_cross==0 & newdat$road_type_notA==1], d$predprob[newdat$road_traffic==0 & newdat$road_cross==0 & newdat$road_type_notA==1], type="l", col="black", lty=1, lwd=2) #
          
points(newdat$road_dist[newdat$road_traffic==20000 & newdat$road_cross==1], d$predprob[newdat$road_traffic==20000 & newdat$road_cross==1], col="red") 
points(newdat$road_dist[newdat$road_traffic==1500 & newdat$road_cross==1], d$predprob[newdat$road_traffic==1500 & newdat$road_cross==1], pch=8, col="blue") 
#points(newdat$log_road_dist[newdat$road_traffic==0 & newdat$road_cross==1 & newdat$road_type_public==0], pred$fit[newdat$road_traffic==0 & newdat$road_cross==1 & newdat$road_type_public==0], pch=16, col="grey") 
points(newdat$road_dist[newdat$road_traffic==0 & newdat$road_cross==1 & newdat$road_type_public==1], d$predprob[newdat$road_traffic==0 & newdat$road_cross==1 & newdat$road_type_public==1], pch=8, col="black") 
          
points(newdat$road_dist[newdat$road_traffic==20000 & newdat$road_cross==0  & newdat$road_dist==0], d$predprob[newdat$road_traffic==20000 & newdat$road_cross==0  & newdat$road_dist==0], pch=16, col="red") 
points(newdat$road_dist[newdat$road_traffic==1500 & newdat$road_cross==0  & newdat$road_dist==0], d$predprob[newdat$road_traffic==1500 & newdat$road_cross==0  & newdat$road_dist==0], pch=16, col="blue") 
#points(newdat$log_road_dist[newdat$road_traffic==0 & newdat$road_cross==0 & newdat$road_type_notA==0  & newdat$road_dist==0], pred$fit[newdat$road_traffic==0 & newdat$road_cross==0 & newdat$road_type_notA==0  & newdat$road_dist==0], pch=1, col="grey") 
points(newdat$road_dist[newdat$road_traffic==0 & newdat$road_cross==0 & newdat$road_type_notA==1  & newdat$road_dist==0], d$predprob[newdat$road_traffic==0 & newdat$road_cross==0 & newdat$road_type_notA==1  & newdat$road_dist==0], pch=16, col="black") 

```


```{r}
hist(dvvv2$road_dist)
```










  
=======
---
title: "SSF: survival package vs. ResourceSeceltion package"
author: "anneMehl"
date: "9 april 2018"
output: word_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



### Old way, using library survival

```{r}
  load("output/dvvv1.rda")

  starttime <- Sys.time()
  mod1_dvvv2 <- coxph(Surv(rep(1, length(use)), use) ~ strata(strat) + pspline(step_length,2) +
                  prop_ar5_agri + prop_ar5_bog + prop_ar5_urban + prop_young_forest + prop_water + slope +
                  prop_airport + crossed_rail + road_cross + fence_cross + dist_passage + log_road_dist + log_road_traffic + road_type_notA + log_road_dist:log_road_traffic + log_road_dist:road_type_notA, data = dvvv2)
  endtime <- Sys.time()
  endtime-starttime
  save(mod1_dvvv2, file="mod1_dvvv2.rda")
  
  # save(mod1, file="mod1.rda")
  load("output/mod1.rda")
  load("output/mod1_dvvv2")
  
  summary(mod1)
  summary(mod1_dvvv2)
```



##### Run Christers coxph model to compare the coefficients  

```{r}
  load("processdata/gpsdata2.rda")

  starttime <- Sys.time()
  mod7chr <- coxph(Surv(rep(1, length(use)), use) ~ strata(strat) + pspline(step_length,2) + 
                  prop_ar5_agri + prop_ar5_bog + prop_ar5_urban + prop_young_forest + prop_water + slope + 
                  prop_airport + crossed_rail + road_cross + fence_cross + dist_passage + log_road_dist + log_road_traffic + road_type_notA + log_road_dist:log_road_traffic + log_road_dist:road_type_notA, data = gpsdata2)
  endtime <- Sys.time()
  endtime-starttime
  # save(mod7chr, file = "mod7chr.rda")
  load("output/mod7chr.rda")
  summary(mod7chr)
```



##### Loading the ssf model run with rspf from the ResourceSeceltion package with 25 bootstraps
```{r}
load("output/mod2_25.rda")
mod2_25 <- mod2
load("processdata/models.rda")# loads mod_ssf and mod_sspf
load("output/mod1.rda")  
load("output/mod2.rda")
load("output/mod7chr.rda")
load("processdata/models2.rda") # loads mod_ssf, mod_sspf, mod_sspfv2, mod_sspfv3 
summary(mod_ssf)
summary(mod_sspf)
summary(mod_sspfV2) # probit link
summary(mod_sspfV3) # c log log link
summary(mod2_25)
```
  
  
##### Compare coefficeints of both (Christers and mine) coxph models AND the two run in ResourceSelection package
Put model estimates into temporary data.frames:

```{r}
  model1frame <- data.frame(Variable = rownames(summary(mod1)$coef),
                            Coefficient = summary(mod1)$coef[, 1],
                            SE = summary(mod1)$coef[, 2],
                            modelname = "mod1")
  
  model7frame <- data.frame(Variable = rownames(summary(mod7chr)$coef),
                            Coefficient = summary(mod7chr)$coef[, 1],
                            SE = summary(mod7chr)$coef[, 2],
                            modelname = "mod7")
  
  modelrspackage <- data.frame(Variable = rownames(summary(mod2)$coef),
                            Coefficient = summary(mod2)$coef[, 1],
                            SE = summary(mod2)$coef[, 2],
                            modelname = "rspackage")
  
  modelrspackage25 <- data.frame(Variable = rownames(summary(mod2_25)$coef),
                            Coefficient = summary(mod2_25)$coef[, 1],
                            SE = summary(mod2_25)$coef[, 2],
                            modelname = "ssfboot")
  
  
  model_ssf <- data.frame(Variable = rownames(summary(mod_ssf)$coef),
                            Coefficient = summary(mod_ssf)$coef[, 1],
                            SE = summary(mod_ssf)$coef[, 2],
                            modelname = "mod_ssf")
  
  model_sspf <- data.frame(Variable = rownames(summary(mod_sspf)$coef),
                            Coefficient = summary(mod_sspf)$coef[, 1],
                            SE = summary(mod_sspf)$coef[, 2],
                            modelname = "mod_sspf")
  
  model_sspfv2 <- data.frame(Variable = rownames(summary(mod_sspfV2)$coef),
                            Coefficient = summary(mod_sspfV2)$coef[, 1],
                            SE = summary(mod_sspfV2)$coef[, 2],
                            modelname = "mod_sspfV2")
  
  model_sspfv3<- data.frame(Variable = rownames(summary(mod_sspfV3)$coef),
                            Coefficient = summary(mod_sspfV3)$coef[, 1],
                            SE = summary(mod_sspfV3)$coef[, 2],
                            modelname = "mod_sspfV3")
  
  modelrspackage$SE <- "0"
  modelrspackage$SE <- as.numeric(modelrspackage$SE)
  model_sspf$SE <- "0"
  model_sspf$SE <- as.numeric( model_sspf$SE)
  model_sspfv2$SE <- "0"
  model_sspfv2$SE <- as.numeric( model_sspfv2$SE)
  model_sspfv3$SE <- "0"
  model_sspfv3$SE <- as.numeric( model_sspfv3$SE)
  
```


Then I combine these data.frames:
```{r}
  allmodelframe <- data.frame(rbind(modelrspackage, model_ssf, model_sspf, model_sspfv2, model_sspfv3))
```


Here, the width of the confidence intervals is being specified
```{r}
  interval1 <- -qnorm((1-0.95)/2)  # 90% multiplier
  interval2 <- -qnorm((1-0.95)/2)  # 95% multiplier
```


```{r figure-setup, echo = FALSE, include = FALSE}
knitr::opts_chunk$set(fig.path = "figs/", fig.width = 6.5,
                      fig.height = 4, fig.align = "center")
```


```{r comparing different ssf-models, fig.cap='Comparing different ssf-models'}
ggplot(allmodelframe, aes(colour = modelname)) + 
    geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) + 
    geom_linerange(aes(x = Variable, ymin = Coefficient - SE*interval1,
                                  ymax = Coefficient + SE*interval1),
                              lwd = 1, position = position_dodge(width = 1/2)) + 
    geom_pointrange(aes(x = Variable, y = Coefficient, ymin = Coefficient - SE*interval2,
                                   ymax = Coefficient + SE*interval2),
                               lwd = 1/2, position = position_dodge(width = 1/2),
                               shape = 21, fill = "WHITE") + coord_flip() + theme_bw() + 
    ggtitle("sspf: comparing different models")

```
  

##### Model selection with AIC
```{r}
AIC(mod2, mod_sspf, mod_sspfV2, mod_sspfV3)
```

  
#### New way, using library ResourceSelection
This bit has been run on Brams computer, because it takes very long
  
```{r}
  ## LOOK FOR STRATS WITH 0, IF IT RETURNS STH, RUN THE CODE BELOW
load("output/dvvv1.rda")
  which(tapply(dvvv1$use, dvvv1$strat, max)==0)
  
  dvvv2 <- dvvv1[!(dvvv1$strat %in% as.numeric(names(which(tapply(dvvv1$use, dvvv1$strat, max)==0)))),]
  which(tapply(dvvv2$use, dvvv2$strat, max)==0)
  head(dvvv2)
  nrow(dvvv2)
  nrow(dvvv1)
  # save(dvvv2, file="dvvv2.rda")
  
  load("output/dvvv2.rda")
  
  starttime <- Sys.time()
  mod2 <- rspf(use~ step_length + prop_ar5_agri + prop_ar5_bog + prop_ar5_urban + prop_young_forest + prop_water + slope + 
                 prop_airport + crossed_rail + road_cross + fence_cross + dist_passage + log_road_dist + log_road_traffic + 
                 road_type_notA + log_road_dist:log_road_traffic + log_road_dist:road_type_notA,
                   data=dvvv2, m=dvvv2$strat, B=0, link="logit")
  endtime <- Sys.time()
  endtime-starttime
  
  # save(mod2, file="mod2.rda")
  
  load("output/mod2.rda")
  str(mod2)
  summary(mod2)
  mep(mod2)
```



##### Plot the effects of the road variables for the ResourceSelection model
Firt we prepare a new data set to simulate or predict some things later in the plots. (?)

```{r}
load("output/mod2_25.rda")
load("output/mod2.rda")
mod2_25 <- mod2
load("output/dvvv2.rda")
tmp <- dvvv2
          newdat <- tmp[rep(1, 2000),] 
          newdat$road_dist <- c(c(0,0:498)*2, c(0,0:498)*2, c(0,0:498)*2, c(0,0:498)*2) #x axis (0=crossing, then from (0=no crossing) to 996 m in steps of 2 - the whole thing repeated 4 times
          newdat$log_road_dist <- log10(newdat$road_dist+1)  
          hist(dvvv2$road_traffic[dvvv2$road_traffic>0])
          quantile(dvvv2$road_traffic[dvvv2$road_traffic>0], 0.25)
          quantile(dvvv2$road_traffic[dvvv2$road_traffic>0], 0.95)
          newdat$road_traffic <- rep(c(0,0,1500,20000), each=500) # we don't predcit traffic in a continuous way - we use cross; no traffic, low, med and high traffic
          newdat$log_road_traffic <- log10(newdat$road_traffic+1)    
          newdat$road_cross <- 0
          newdat$road_cross[c(1,501, 1001, 1501)] <- 1
          newdat$road_cross <- as.factor(newdat$road_cross)
          newdat$road_type_notA <- 0
          newdat$road_type_notA[c(1:500)] <- 1
          newdat$road_type_notA <- as.factor(newdat$road_type_notA)
          
library("boot", lib.loc="~/R/win-library/3.4")
d <- newdat
m <- mod_sspf

#  I think that model.matrix will generate automatically the columns that you need, give it a try:

d <- na.omit(d)

X <- model.matrix(m$formula, data=d)
    
predvals <- (X %*% coef(m)[match(colnames(X), names(coef(m)))])[,1]
     
d$linpred <- predvals
d$predprob <- inv.logit(d$linpred)
head(d)

```



###### Version without log transforming distance to road:        
```{r}
#    xlab="log distance to road", ylab="step selection") 
# high traffic volume (20000) and no possibility for road crossing (0)
plot(newdat$road_dist[newdat$road_traffic==20000 & newdat$road_cross==0], d$predprob[newdat$road_traffic==20000 & newdat$road_cross==0], type="l", col="red", ylim=c(0,0.0002), xlim = c(),
xlab="Avstand til veg (meter)", ylab="Strekningsvalg", cex.lab=1.5, cex.axis=1.1, lty=1, lwd=2) #

lines(newdat$road_dist[newdat$road_traffic==1500 & newdat$road_cross==0], d$predprob[newdat$road_traffic==1500 & newdat$road_cross==0], type="l", col="blue", lty=1.5, lwd=2) #
#lines(newdat$log_road_dist[newdat$road_traffic==0 & newdat$road_cross==0 & newdat$road_type_notA==0], pred$fit[newdat$road_traffic==0 & newdat$road_cross==0 & newdat$road_type_notA==0], type="l", col="grey") # predictionif we really had zero traffic - wihc is quite impossible. Also, we predict outside the range - we get artefacts
lines(newdat$road_dist[newdat$road_traffic==0 & newdat$road_cross==0 & newdat$road_type_notA==1], d$predprob[newdat$road_traffic==0 & newdat$road_cross==0 & newdat$road_type_notA==1], type="l", col="black", lty=1, lwd=2) #
          
points(newdat$road_dist[newdat$road_traffic==20000 & newdat$road_cross==1], d$predprob[newdat$road_traffic==20000 & newdat$road_cross==1], col="red") 
points(newdat$road_dist[newdat$road_traffic==1500 & newdat$road_cross==1], d$predprob[newdat$road_traffic==1500 & newdat$road_cross==1], pch=8, col="blue") 
#points(newdat$log_road_dist[newdat$road_traffic==0 & newdat$road_cross==1 & newdat$road_type_public==0], pred$fit[newdat$road_traffic==0 & newdat$road_cross==1 & newdat$road_type_public==0], pch=16, col="grey") 
points(newdat$road_dist[newdat$road_traffic==0 & newdat$road_cross==1 & newdat$road_type_public==1], d$predprob[newdat$road_traffic==0 & newdat$road_cross==1 & newdat$road_type_public==1], pch=8, col="black") 
          
points(newdat$road_dist[newdat$road_traffic==20000 & newdat$road_cross==0  & newdat$road_dist==0], d$predprob[newdat$road_traffic==20000 & newdat$road_cross==0  & newdat$road_dist==0], pch=16, col="red") 
points(newdat$road_dist[newdat$road_traffic==1500 & newdat$road_cross==0  & newdat$road_dist==0], d$predprob[newdat$road_traffic==1500 & newdat$road_cross==0  & newdat$road_dist==0], pch=16, col="blue") 
#points(newdat$log_road_dist[newdat$road_traffic==0 & newdat$road_cross==0 & newdat$road_type_notA==0  & newdat$road_dist==0], pred$fit[newdat$road_traffic==0 & newdat$road_cross==0 & newdat$road_type_notA==0  & newdat$road_dist==0], pch=1, col="grey") 
points(newdat$road_dist[newdat$road_traffic==0 & newdat$road_cross==0 & newdat$road_type_notA==1  & newdat$road_dist==0], d$predprob[newdat$road_traffic==0 & newdat$road_cross==0 & newdat$road_type_notA==1  & newdat$road_dist==0], pch=16, col="black") 

```


```{r}
hist(dvvv2$road_dist)
```










  
>>>>>>> 33073c58e577f151a44cf063f78edd1b3c2e3689
  