---
title: "06_prep_stack"
author: "anne"
date: "16 september 2019"
output: word_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load libraries 
```{r}

library(raster)
# library(RPostgreSQL)
# library(rpostgis)
```


## Intersect each variable 
```{r}
# From Bram (code) ====


# log_dist_building 
drv <- dbDriver("PostgreSQL") # driver
con <- dbConnect(drv, dbname="NINA_SPATIAL", host="ninpgsql04.nina.no",  
                 port="5432", user='postgres', password='PsmaWT6mJ8RdkFu') # define connection

buildings <- pgGetGeom(con, c("N50_Norge","N50_byggoganlegg_p"), geom = "geom", 
                  clauses = "WHERE (byggtyp_nb > 0 AND byggtyp_nb < 161) OR 
                                                                          (byggtyp_nb > 163 AND byggtyp_nb < 171) OR
                                                                          (byggtyp_nb > 172 AND byggtyp_nb < 181) OR
                                                                          (byggtyp_nb > 183 AND byggtyp_nb < 214) OR
                                                                          (byggtyp_nb > 214 AND byggtyp_nb < 216) OR
                                                                          (byggtyp_nb > 216 AND byggtyp_nb < 221) OR
                                                                          (byggtyp_nb > 221 AND byggtyp_nb < 223) OR
                                                                          (byggtyp_nb > 223 AND byggtyp_nb < 229) OR
                                                                          (byggtyp_nb > 229 AND byggtyp_nb < 830) OR
                                                                          (byggtyp_nb > 830 AND byggtyp_nb < 840) OR
                                                                          (byggtyp_nb > 840 AND byggtyp_nb < 956) OR
                                                                          byggtyp_nb > 956", boundary = NULL, query = NULL)

buildings <- spTransform(buildings, crs(slope))
plot(slope)
plot(buildings, add=T)
build <- rasterize(buildings, slope, 'byggtyp_nb', fun='first')
build_dist <- distance(build)
plot(build_dist)
writeRaster(build_dist, "maps/dist_building.tif")

# log_road_dist, road_cross, & road_traffic_high 
# traffic_high - adt>5000 - takes > 1.5 hours #

drv <- dbDriver("PostgreSQL") # driver
con <- dbConnect(drv, dbname="env_database", host="ninpgsql04.nina.no",  
                 port="5432", user='postgres', password='PsmaWT6mJ8RdkFu') # define connection

traffic <- pgGetGeom(con, c("vegvesen","road_traffic"), geom = "geom", 
                       clauses = "WHERE adt_total>5000", boundary = NULL, query = NULL)

plot(slope)
traffic <- spTransform(traffic, crs(slope))
plot(traffic, lwd=2, col="red", add=T)

# all roads - takes > 40 hours #

roads <- pgGetGeom(con, c("vegvesen","roads_2015"), geom = "geom")
roads <- spTransform(roads, crs(slope))
plot(roads, col="blue", add=T)

dbDisconnect(con)
dbUnloadDriver(drv)

traffic_rast <- rasterize(traffic, slope)
plot(traffic_rast)
traffic_dist <- distance(traffic_rast)
plot(traffic_dist)
writeRaster(traffic_dist, "maps/dist_road_traffic_high.tif")

roads_rast <- rasterize(roads, slope)
roads_dist <- distance(roads_rast)
writeRaster(roads_dist, "maps/dist_roads.tif")

traffic_dist <- raster("maps/dist_road_traffic_high.tif")
roads_dist <- raster("maps/dist_roads.tif")
plot(roads_dist)

# From Bram (maps) ====

# building and roads, traffic
roads_dist <- raster("maps/dist_roads.tif")
traffic_dist <- raster("maps/dist_road_traffic_high.tif")
building_dist <- raster("maps/dist_building.tif")

# prop_young_forest 
young <- raster("maps/prop_young_forest.tif")
hist(young)

# prop_old_forest 
old <- raster("maps/prop_old_forest.tif")
hist(old)



# AR5 maps =====

water <- raster("maps/ar5_4_water.tif")
agri <- raster("maps/ar5_1_agri.tif")
ruderal <- raster("maps/ar5_2_ruderal.tif")
bog <- raster("maps/ar5_3_bog.tif")
urban <- raster("maps/ar5_5_urban.tif")
mprodcon <- raster("maps/ar5_9_mprod_conifer.tif")
lprodcon <- raster("maps/ar5_10_lprod_conifer.tif")
decforest <- raster("maps/ar5_11_dec_forest.tif")
mixforest <- raster("maps/ar5_12_mix_forest.tif")

```

## look at the resolution of the layers
```{r}
res(building_dist)
res(roads_dist)
res(water)
res(agri)
res(ruderal)
res(bog)
res(urban)
res(mprodcon)
res(lprodcon)
res(decforest)
res(mixforest)
res(traffic_dist)
res(young)
res(old)


# resampled map layers --> Don't need this anymore, since I made the new RasterLayers for AR5
# res(water_rs)
# res(agri_rs)
# res(ruderal_rs)
# res(bog_rs)
# res(urban_rs)
# res(mprodcon_rs)
# res(lprodcon_rs)
# res(decforest_rs)
# res(mixforest_rs)

```

<!-- Resample map layers, so that they have same resolution -->
<!-- ```{r} -->
<!-- water_rs <- resample(water, young, method = "ngb") -->
<!-- agri_rs <- resample(agri, young, method = "ngb") -->
<!-- ruderal_rs <- resample(ruderal, young, method = "ngb") -->
<!-- bog_rs <- resample(bog, young, method = "ngb") -->
<!-- urban_rs <- resample(urban, young, method = "ngb") -->
<!-- mprodcon_rs <- resample(mprodcon, young, method = "ngb") -->
<!-- lprodcon_rs <- resample(lprodcon, young, method = "ngb") -->
<!-- decforest_rs <- resample(decforest, young, method = "ngb") -->
<!-- mixforest_rs <- resample(mixforest, young, method = "ngb") -->

<!-- ``` -->



## plot the layers
```{r}
plot(roads_dist)
plot(building_dist)
plot(traffic_dist)
plot(young)
plot(old)

plot(water)
plot(agri)
plot(ruderal)
plot(bog)
plot(urban)
plot(mprodcon)
plot(lprodcon)
plot(decforest)
plot(mixforest)

```


## Re-classify AR5 map, so it includes all counties needed
reclassify ar5clip from Bram -> use Christers script for guidance

```{r}
AR5 <- raster("maps/AR5clip.tif")
res(AR5)
str(AR5)


m <- c(1,1,  2,1,  3,1,  4,8,  5,11,  6,12,  7,3,  8,3,  9,3,  10,8,  11,11,  12,12,  13,3,  14,3,  15,3,  16,9,  17,11,  18,12,  19,3,  20,3,  21,3,  22,10,  23,11,  24,12,  25,3,  26,3,  27,10,  28,11,  29,12,  30,3,  31,3,  32,3,  33,3,  34,2,  35,5,  36,6,  37,13,  38,4,  39,7)

rclmat <- matrix(m, ncol = 2, byrow = TRUE)

ar5_rc <- reclassify(AR5, rclmat)
writeRaster(ar5_rc, "maps/ar5_rc.tif", overwrite = T)

ar5_rc <- raster("maps/ar5_rc.tif")
plot(ar5_rc)
print(ar5_rc)


```

## Write rasters for each value (AR5 class)

#### change memory size  
Maybe it is necessary to extend the memory limit, because the models are quite large.
This is how it is done. It re-sets itself when the R-session is terminated.
```{r}
# To check the current memory limit
memory.limit() #[1] 8062 -----> default
# To check the current size (only when not changed) and to change the memory limit
memory.size(20000) # Put the new memory size into the bracktes, e.g. 9000
```

#### write rasters
```{r}

rast1 <- ar5_rc
rast2 <- ar5_rc
rast3 <- ar5_rc
rast4 <- ar5_rc
rast5 <- ar5_rc
rast6 <- ar5_rc
rast7 <- ar5_rc
rast8 <- ar5_rc
rast9 <- ar5_rc
rast10 <- ar5_rc
rast11 <- ar5_rc
rast12 <- ar5_rc
rast13 <- ar5_rc

values(rast1) <- ifelse(values(rast1)==1, 1, 0)
writeRaster(rast1, "ar5_1_agri.tif", overwrite=TRUE)

values(rast2) <- ifelse(values(rast2)==2, 1, 0)
writeRaster(rast2, "ar5_2_ruderal.tif", overwrite=TRUE)

values(rast3) <- ifelse(values(rast3)==3, 1, 0)
writeRaster(rast3, "ar5_3_bog.tif", overwrite=TRUE)

values(rast4) <- ifelse(values(rast4)==4, 1, 0)
writeRaster(rast4, "ar5_4_water.tif", overwrite=TRUE)

values(rast5) <- ifelse(values(rast5)==5, 1, 0)
writeRaster(rast5, "ar5_5_urban.tif", overwrite=TRUE)

# values(rast6) <- ifelse(values(rast6)==6, 1, 0)
# writeRaster(rast6, "ar5_6_samferdsel.tif", overwrite=TRUE)
# 
# values(rast7) <- ifelse(values(rast7)==7, 1, 0)
# writeRaster(rast7, "ar5_7_not_mapped.tif", overwrite=TRUE)
# 
# values(rast8) <- ifelse(values(rast8)==8, 1, 0)
# writeRaster(rast8, "ar5_8_hprod_conifer.tif", overwrite=TRUE)

values(rast9) <- ifelse(values(rast9)==9, 1, 0)
writeRaster(rast9, "ar5_9_mprod_conifer.tif", overwrite=TRUE)

values(rast10) <- ifelse(values(rast10)==10, 1, 0)
writeRaster(rast10, "ar5_10_lprod_conifer.tif", overwrite=TRUE)

values(rast11) <- ifelse(values(rast11)==11, 1, 0)
writeRaster(rast11, "ar5_11_dec_forest.tif", overwrite=TRUE)

values(rast12) <- ifelse(values(rast12)==12, 1, 0)
writeRaster(rast12, "ar5_12_mix_forest.tif", overwrite=TRUE)

# values(rast13) <- ifelse(values(rast13)==13, 1, 0)
# writeRaster(rast13, "ar5_13_glacier.tif", overwrite=TRUE)


```


## Check if the maps have the same projection and extend
```{r}
projection(old)
projection(water)

extend(young)
extend(agri)

xmin(young)
xmin(agri)
ymin(young)
ymin(agri)


```

#### Crop new ar5 raster layers to the same extend as the ones from Brams sspf
```{r}
agricrop <- crop(x = agri, y = young)
writeRaster(agricrop, "maps/new/ar5_1_agri.tif", overwrite=TRUE)

ruderalcrop <- crop(ruderal, young)
writeRaster(ruderalcrop, "maps/new/ar5_2_ruderal.tif", overwrite=TRUE)

bogcrop <- crop(bog, young)
writeRaster(bogcrop, "maps/new/ar5_3_bog.tif", overwrite=TRUE)

watercrop <- crop(water, young)
writeRaster(watercrop, "maps/new/ar5_4_water.tif", overwrite=TRUE)

urbancrop <- crop(urban, young)
writeRaster(urbancrop, "maps/new/ar5_5_urban.tif", overwrite=TRUE)

mprodconcrop <- crop(mprodcon, young)
writeRaster(mprodconcrop, "maps/new/ar5_9_mprod_conifer.tif", overwrite=TRUE)

lprodconcrop <- crop(lprodcon, young)
writeRaster(lprodconcrop, "maps/new/ar5_10_lprod_conifer.tif", overwrite=TRUE)

decforestcrop <- crop(decforest, young)
writeRaster(decforestcrop, "maps/new/ar5_11_dec_forest.tif", overwrite=TRUE)

mixforestcrop <- crop(mixforest, young)
writeRaster(mixforestcrop, "maps/new/ar5_12_mix_forest.tif", overwrite=TRUE)

```


```{r}
# par(mfrow=c(1,2))
plot(young)
plot(watercrop)
```

