---
title: "07_qualitymap"
author: "anne"
date: "16 september 2019"
output: word_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Make raster stack 

#### load libraries and rasters
```{r}
# Load libraries 
library(raster)

# Load rasters 
roads_dist <- raster("maps/dist_roads.tif")
traffic_dist <- raster("maps/dist_road_traffic_high.tif")
building_dist <- raster("maps/dist_building.tif")
young <- raster("maps/prop_young_forest.tif")
old <- raster("maps/prop_old_forest.tif")

water_rs <- raster("maps/ar5_resampled/ar5_4_water.tif")
agri_rs <- raster("maps/ar5_resampled/ar5_1_agri.tif")
ruderal_rs <- raster("maps/ar5_resampled/ar5_2_ruderal.tif")
bog_rs <- raster("maps/ar5_resampled/ar5_3_bog.tif")
urban_rs <- raster("maps/ar5_resampled/ar5_5_urban.tif")
mprodcon_rs <- raster("maps/ar5_resampled/ar5_9_mprod_conifer.tif")
lprodcon_rs <- raster("maps/ar5_resampled/ar5_10_lprod_conifer.tif")
decforest_rs <- raster("maps/ar5_resampled/ar5_11_dec_forest.tif")
mixforest_rs <- raster("maps/ar5_resampled/ar5_12_mix_forest.tif")

```

#### Transform layers 
```{r}

log_dist_building <- raster("maps/dist_building.tif")
values(log_dist_building) <- log10(values(log_dist_building) + 1)
# plot(log_dist_building)


log_road_dist <- raster("maps/dist_roads.tif")
values(log_road_dist) <- log10(values(log_road_dist)+1)
# plot(log_road_dist)

dist_roads <- raster("maps/dist_roads.tif")
road_traffic_high <- raster("maps/dist_road_traffic_high.tif")
values(road_traffic_high) <- ifelse(values(dist_roads) < values(road_traffic_high),0,1)
# plot(road_traffic_high)

interaction <- road_traffic_high
values(interaction) <- values(log_road_dist)*values(road_traffic_high)
# plot(interaction)


```



## Make brick --> needs to be in the same order as model variables in model
```{r}
mybrick <- log_dist_building
mybrick <- brick(mybrick)
mybrick <- addLayer(mybrick, log_road_dist)
mybrick <- addLayer(mybrick, water_rs )
mybrick <- addLayer(mybrick, agri_rs)
mybrick <- addLayer(mybrick, ruderal_rs)
mybrick <- addLayer(mybrick, bog_rs)
mybrick <- addLayer(mybrick, urban_rs)
mybrick <- addLayer(mybrick, mprodcon_rs)
mybrick <- addLayer(mybrick, lprodcon_rs)
mybrick <- addLayer(mybrick, decforest_rs)
mybrick <- addLayer(mybrick, mixforest_rs)
mybrick <- addLayer(mybrick, road_traffic_high)
mybrick <- addLayer(mybrick, old)
mybrick <- addLayer(mybrick, young)
mybrick <- addLayer(mybrick, interaction)

# airport <- raster("maps/prop_airport.tif") # for posthoc removal



```



## Predict

#### LOad libraries
```{r}
library(ResourceSelection)
library(boot)
```

#### Load model
```{r}
load("output/mod11c_rspf_99boot.rda")
rspf_mod <- mod11c_rspf_99boot
coefs <- rspf_mod$coefficients
```

#### Make newdat
```{r}
newdat <- as.data.frame(mybrick)
newdat <- data.frame(intercept=1, newdat) # makes an intercept column
str(newdat)
# newdat[,3] <- as.numeric(newdat[,3])
# table(newdat[,3])
# newdat[,3] <- ifelse(newdat[,3]==1, 0, 1)
# str(newdat)
# 
# tmp <- newdat[,15]
# sum(is.na(tmp)) #I don't get it, but it seems to correspond with the values of 800
# newdat[,15] <- as.numeric(newdat[,15])
# newdat[,15] <- ifelse(is.na(tmp), 800, 0)
# table(newdat[,15])
# str(newdat)

newdat <- as.matrix(newdat)
head(newdat)

```

#### change memory size  
Maybe it is necessary to extend the memory limit, because the models are quite large.
This is how it is done. It re-sets itself when the R-session is terminated.
```{r}
# To check the current memory limit
memory.limit() #[1] 8062 -----> default
# To check the current size (only when not changed) and to change the memory limit
memory.size(30000) # Put the new memory size into the bracktes, e.g. 9000
```
  

#### Predict
```{r}
predvals <- (newdat %*% coefs)

linpred <- predvals[,1]
predprob <- inv.logit(linpred)

```

#### Make and write raster
```{r}
young <- young # just use any layer, raster("maps/prop_young_forest.tif")

quality <- young
values(quality) <- predprob
plot(quality)

writeRaster(quality, "maps/quality2.tif", overwrite = T)

# permeability <- raster("maps/permeability.tif")
# plot(permeability)

```





## Prepare smaller maps of habitat quality and landscape friction to test Habitat functionality, so it runs faster

```{r}
library(raster)

permeability <- raster("maps/permeability.tif")
# permeability2 <- raster("maps/permeability.tif")
quality <- raster("maps/quality.tif")

```

```{r}
plot(permeability)
plot(quality)

e <- drawExtent()

p_crop <- crop(permeability, e)
plot(p_crop)

qu_crop <- crop(quality, e)
plot(qu_crop)

```


```{r}

p1 <- aggregate(permeability)
p2 <- aggregate(permeability, fact = 20)
p3 <- aggregate(p_crop, fact = 20)

q1 <- aggregate(quality)
q2 <- aggregate(qu_crop, fact = 20)

```

```{r}
res(permeability)
res(p_crop)
# res(p2)
res(p3)

str(p_crop)
str(p2)
str(p3)

res(quality)
res(qu_crop)
res(q2)

str(qu_crop)
str(q2)

```


```{r}

par(mfrow = c(2, 2))
plot(p_crop)
plot(p3)

plot(qu_crop)
plot(q2)


```

```{r}
writeRaster(p3, "maps/permeability_coarse.tif", overwrite = T)
writeRaster(q2, "maps/quality_coarse.tif", overwrite = T)

```

```{r}
p_coarse <- raster("maps/permeability_coarse.tif")
q_coarse <- raster("maps/quality_coarse.tif")

plot(p)
plot(q)

writeRaster(p, "maps/permeability_coarse.asc", overwrite = T)
writeRaster(q, "maps/quality_coarse.asc", overwrite = T)

```


## Prepare maps in a higher resolution (for both quality and permeability)
```{r}
library(raster)

permeability <- raster("maps/permeability.tif")
# permeability2 <- raster("maps/permeability.tif")
quality <- raster("maps/quality.tif")
# 
# permeability_2 <- raster("maps/p233_s.tif")
# quality_2 <- raster("maps/q233_s.tif")

```

```{r}
res(permeability)
str(permeability)
str(p_coarse)

res(quality)
str(quality)
str(q_coarse)

```

```{r}
plot(permeability)
e <- drawExtent()

p_crop2 <- crop(permeability, e)
plot(p_crop2)

qu_crop2 <- crop(quality, e)
plot(qu_crop2)

writeRaster(p_crop2, "maps/p_crop2.tif", overwrite = T)
writeRaster(qu_crop2, "maps/qu_crop2.tif", overwrite = T)
```

```{r}
p1 <- aggregate(permeability, fact = 50)
p2 <- aggregate(permeability, fact = 15)
p460 <- aggregate(permeability, fact = 20) # too "large"
p580 <- aggregate(permeability, fact = 25) # still too "large"

p210_s <- aggregate(p_crop2, fact = 9)

q460 <- aggregate(quality, fact = 20) # too "large"
q580 <- aggregate(quality, fact = 25) # still too "large"
q210_s <- aggregate(qu_crop2, fact = 9)

```

```{r}
res(permeability)
res(p186_s)
str(p_s)
str(permeability)

res(quality)
str(quality)
str(q460_s)

```

```{r}
writeRaster(p210_s, "maps/p210_s.asc", overwrite = T)
writeRaster(q210_s, "maps/q210_s.asc", overwrite = T)
```

