---
title: "07_qualitymap"
author: "anne"
date: "16 september 2019"
output: word_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Make raster stack 

#### load libraries and rasters
```{r}
# Load libraries 
library(raster)

# Load rasters 


```

#### Transform layers 
```{r}

log_dist_building <- raster("maps/dist_building.tif")
values(log_dist_building) <- log(values(log_dist_building) + 1)
plot(log_dist_building)


log_road_dist <- raster("maps/dist_roads.tif")
values(log_road_dist) <- log(values(log_road_dist)+1)
plot(log_road_dist)

dist_roads <- raster("maps/dist_roads.tif")
road_traffic_high <- raster("maps/dist_road_traffic_high.tif")
values(road_traffic_high) <- ifelse(values(dist_roads) < values(road_traffic_high),0,1)
plot(road_traffic_high)

interaction <- road_traffic_high
values(interaction) <- values(log_road_dist)*values(road_traffic_high)
plot(interaction)


```



## Make brick --> needs to be in the same order as model variables in model
```{r}
mybrick <- log_dist_building
mybrick <- brick(mybrick)
mybrick <- addLayer(mybrick, log_road_dist)
mybrick <- addLayer(mybrick, water, agri, ruderal, bog, urban,  mprodcon, lprodcon,  decforest, mixforest)
mybrick <- addLayer(mybrick, road_traffic_high)
mybrick <- addLayer(mybrick, old)
mybrick <- addLayer(mybrick, young)
mybrick <- addLayer(mybrick, interaction)

# airport <- raster("maps/prop_airport.tif") # for posthoc removal

```



## Predict

#### LOad libraries
```{r}
library(ResourceSelection)
library(boot)
```

#### Load model
```{r}
load("outputs/mod11c_rspf_99boot.rda")
rspf_mod <- mod11c_rspf_99boot
coefs <- rspf_mod$coefficients
```

#### Make newdat
```{r}
newdat <- as.data.frame(mybrick)
newdat <- data.frame(intercept=1, newdat) # makes an intercept column
str(newdat)
# newdat[,3] <- as.numeric(newdat[,3])
# table(newdat[,3])
# newdat[,3] <- ifelse(newdat[,3]==1, 0, 1)
# str(newdat)
# 
# tmp <- newdat[,15]
# sum(is.na(tmp)) #I don't get it, but it seems to correspond with the values of 800
# newdat[,15] <- as.numeric(newdat[,15])
# newdat[,15] <- ifelse(is.na(tmp), 800, 0)
# table(newdat[,15])
# str(newdat)

newdat <- as.matrix(newdat)
head(newdat)

```

#### change memory size  
Maybe it is necessary to extend the memory limit, because the models are quite large.
This is how it is done. It re-sets itself when the R-session is terminated.
```{r}
# To check the current memory limit
memory.limit() #[1] 8062 -----> default
# To check the current size (only when not changed) and to change the memory limit
memory.size(30000) # Put the new memory size into the bracktes, e.g. 9000
```
  

#### Predict
```{r}
predvals <- (newdat %*% coefs)

linpred <- predvals[,1]
predprob <- inv.logit(linpred)

```

#### Make and write raster
```{r}
young <- young # just use any layer

permeability <- young
values(permeability) <- predprob
plot(permeability)

writeRaster(permeability, "maps/permeability.tif", overwrite = T)
```

