---
title: "07_qualitymap"
author: "anne"
date: "16 september 2019"
output: word_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## change memory size  
Maybe it is necessary to extend the memory limit, because the models are quite large.
This is how it is done. It re-sets itself when the R-session is terminated.
```{r}
# To check the current memory limit
memory.limit() #[1] 8062 -----> default
# To check the current size (only when not changed) and to change the memory limit
memory.size(30000) # Put the new memory size into the bracktes, e.g. 9000
```


## Make raster stack 

#### Load libraries
```{r}
library(ResourceSelection)
library(boot)
library(raster)
```

#### load rasters
```{r}
# Load rasters 
## Try also remove roads here
roads_dist <- raster("maps/dist_roads.tif")
values(roads_dist) <- 900 # 900 = quantile 99% road_dist
road_traffic_high <- raster("maps/dist_road_traffic_high.tif")
values(road_traffic_high) <- 0
building_dist <- raster("maps/dist_building.tif")
# values(building_dist) <- 0
young <- raster("maps/prop_young_forest.tif")
old <- raster("maps/prop_old_forest.tif")

water_rs <- raster("maps/ar5_resampled/ar5_4_water.tif")
agri_rs <- raster("maps/ar5_resampled/ar5_1_agri.tif")
# values(agri_rs) <- 0
ruderal_rs <- raster("maps/ar5_resampled/ar5_2_ruderal.tif")
# values(ruderal_rs) <- 0
bog_rs <- raster("maps/ar5_resampled/ar5_3_bog.tif")
urban_rs <- raster("maps/ar5_resampled/ar5_5_urban.tif")
# values(urban_rs) <- 0
mprodcon_rs <- raster("maps/ar5_resampled/ar5_9_mprod_conifer.tif")
lprodcon_rs <- raster("maps/ar5_resampled/ar5_10_lprod_conifer.tif")
decforest_rs <- raster("maps/ar5_resampled/ar5_11_dec_forest.tif")
mixforest_rs <- raster("maps/ar5_resampled/ar5_12_mix_forest.tif")

```


#### Aggrigate map layers to chosen resolution
```{r}
## Example
# newLayer <- aggregate(currentLayer, fact = 4, fun = mean) # 4 (93m), 3 (70m) = for stationary, 6 for migratory,  fun can be: mean, modal, min or max

## quality
roads_dist <- aggregate(roads_dist, fact = 4, fun = min) # min?
road_traffic_high <- aggregate(road_traffic_high, fact = 4, fun = max) # max?
building_dist <- aggregate(building_dist, fact = 4, fun = mean)

young <- aggregate(young, fact = 4, fun = mean)
old <- aggregate(old, fact = 4, fun = mean)

# interaction <- aggregate(interaction, fact = 5, fun = mean)
water_rs <- aggregate(water_rs, fact = 4, fun = mean)
agri_rs <- aggregate(agri_rs, fact = 4, fun = mean)
ruderal_rs <- aggregate(ruderal_rs, fact = 4, fun = mean)
bog_rs <- aggregate(bog_rs, fact = 4, fun = mean)
urban_rs <- aggregate(urban_rs, fact = 4, fun = mean)
mprodcon_rs <- aggregate(mprodcon_rs, fact = 4, fun = mean)
lprodcon_rs <- aggregate(lprodcon_rs, fact = 4, fun = mean)
decforest_rs <- aggregate(decforest_rs, fact = 4, fun = mean)
mixforest_rs <- aggregate(mixforest_rs, fact = 4, fun = mean)

```


#### Transform layers 
```{r}

log_dist_building <- building_dist
### When removing buildings, don't run this
values(log_dist_building) <- log10(values(log_dist_building) + 1)


log_road_dist <- roads_dist
values(log_road_dist) <- log10(values(log_road_dist)+1)

interaction <- road_traffic_high


### When removing roads, don't run this
# values(road_traffic_high) <- ifelse(values(roads_dist) < values(road_traffic_high),0,1)
# values(interaction) <- values(log_road_dist)*values(road_traffic_high)



```



## Make brick --> needs to be in the same order as model variables in model
```{r}
mybrick <- log_dist_building
mybrick <- brick(mybrick)
mybrick <- addLayer(mybrick, log_road_dist)
mybrick <- addLayer(mybrick, water_rs )
mybrick <- addLayer(mybrick, agri_rs)
mybrick <- addLayer(mybrick, ruderal_rs)
mybrick <- addLayer(mybrick, bog_rs)
mybrick <- addLayer(mybrick, urban_rs)
mybrick <- addLayer(mybrick, mprodcon_rs)
mybrick <- addLayer(mybrick, lprodcon_rs)
mybrick <- addLayer(mybrick, decforest_rs)
mybrick <- addLayer(mybrick, mixforest_rs)
mybrick <- addLayer(mybrick, road_traffic_high)
mybrick <- addLayer(mybrick, old)
mybrick <- addLayer(mybrick, young)
mybrick <- addLayer(mybrick, interaction)

# airport <- raster("maps/prop_airport.tif") # for posthoc removal



```



## Predict

#### Load model
```{r}
load("output/mod11c_rspf_99boot_new.rda")

# rspf(use ~ log_dist_building + log_road_dist + ar5_rec_new + traffic_high + 
#                               forestage_cat + log_road_dist:traffic_high, 
#                             data = datrsf8, m = datrsf8$id, B = 99, link = "logit")


rspf_mod <- mod11c_rspf_99boot_new
coefs <- rspf_mod$coefficients
```

#### Make newdat
```{r}
newdat <- as.data.frame(mybrick)
newdat <- data.frame(intercept=1, newdat) # makes an intercept column
str(newdat)


newdat <- as.matrix(newdat)
head(newdat)

```
  

#### Predict
```{r}
predvals <- (newdat %*% coefs)

linpred <- predvals[,1]
predprob <- inv.logit(linpred)

```

#### Make and write raster
```{r}

quality_without_roads_1501 <- young # just use any layer, raster("maps/prop_young_forest.tif")
values(quality_without_roads_1501) <- predprob

# plot(quality_without_humans_1501)
# res(quality_without_humans_1501)

# writeRaster(quality_without_humans_1501, "maps/quality_without_humans_1501.tif", overwrite = F)

# permeability <- raster("maps/permeability.tif")
# plot(permeability)
quality5 <- raster("maps/quality5.tif")
quality6_0804 <- raster("maps/quality6_0804.tif")
quality6_without_humans_0806 <- raster("maps/quality6_without_humans_0806.tif")
quality6_without_roads_0806 <- raster("maps/quality6_without_roads_0806.tif")
quality6_without_humans_2_0806 <- raster("maps/quality6_without_humans_2_0806.tif")

quality_without_humans_1501 <- raster("maps/quality_without_humans_1501.tif")

```


```{r}

writeRaster(quality_without_roads_1501, "maps/quality_without_roads_1501.asc", overwrite = F)

```









## ###################### OLD!! ################### Extent is drawn together with permeability in permeability script!
#### Draw the extent of the new maps
```{r}
# Use this...
quality6_stationary_30_03_20 <- raster("maps/quality6_stationary_30_03_20.asc")

# ... or this to crop
plot(quality6_0804)
e <- drawExtent()

quality_stationary_test3 <- crop(quality_stationary_test2, e)

# crop_quality6_stationary <- crop(crop_quality6_stationary, e)

plot(quality_stationary_test3)
res(quality_stationary_test3)
# ncols: 246, nrows: 164
```


```{r}

writeRaster(quality_stationary_test3, "maps/quality_stationary_test3.asc", overwrite = F)

```








## Prepare smaller maps of habitat quality and landscape friction to test Habitat functionality, so it runs faster

```{r}
library(raster)

permeability <- raster("maps/permeability.tif")
# permeability2 <- raster("maps/permeability.tif")
quality <- raster("maps/quality.tif")

```
#### Draw the extent of the new maps
```{r}
plot(permeability)
plot(quality)

e <- drawExtent()

p_crop <- crop(permeability, e)
plot(p_crop)

qu_crop <- crop(quality, e)
plot(qu_crop)

```

#### Make coarse maps for trying
```{r}

p1 <- aggregate(permeability)
p2 <- aggregate(permeability, fact = 20)
p3 <- aggregate(p_crop, fact = 20)

q1 <- aggregate(quality)
q2 <- aggregate(qu_crop, fact = 20)

```

```{r}
res(permeability)
res(p_crop)
# res(p2)
res(p3)

str(p_crop)
str(p2)
str(p3)

res(quality)
res(qu_crop)
res(q2)

str(qu_crop)
str(q2)

```


```{r}

par(mfrow = c(2, 2))
plot(p_crop)
plot(p3)

plot(qu_crop)
plot(q2)


```

```{r}
writeRaster(p3, "maps/permeability_coarse.tif", overwrite = T)
writeRaster(q2, "maps/quality_coarse.tif", overwrite = T)

```

```{r}
p_coarse <- raster("maps/permeability_coarse.tif")
q_coarse <- raster("maps/quality_coarse.tif")

plot(p)
plot(q)

writeRaster(p, "maps/permeability_coarse.asc", overwrite = T)
writeRaster(q, "maps/quality_coarse.asc", overwrite = T)

```


## Prepare maps in a higher resolution (for both quality and permeability)
```{r}
library(raster)

permeability <- raster("maps/permeability.tif")
permeability2 <- raster("maps/p93_stationary.asc")
p_crop_migratory3 <- raster("maps/p_crop_migratory3.tif")

quality <- raster("maps/quality3.tif")
quality_2 <- raster("maps/q187_migratory3.asc")
qu_crop_migratory3 <- raster("maps/qu_crop_migratory3.tif")

```

```{r}
res(permeability2)
str(permeability2)
str(p_coarse)

res(quality2)
str(quality)
str(quality_2)

```

#### Draw the extent of the new maps
```{r}
plot(permeability)
e <- drawExtent()

p_crop_stationary <- crop(permeability, e)
plot(p_crop_stationary)

qu_crop_stationary <- crop(quality, e)
plot(qu_crop_stationary)


writeRaster(p_crop_stationary, "maps/p_crop_stationary.tif", overwrite = T)
writeRaster(qu_crop_stationary, "maps/qu_crop_stationary.tif", overwrite = T)

```

```{r}
p1 <- aggregate(permeability, fact = 50)

p93_stationary <- aggregate(p_crop_stationary, fact = 4)



q1 <- aggregate(quality, fact = 50) 

q93_stationary <- aggregate(qu_crop_stationary, fact = 4)




```

```{r}
res(permeability)
res(p_stationary)

str(p_s)
str(q187_migratory3)

res(p187_s)
str(quality)


```

```{r}

writeRaster(p93_stationary, "maps/p93_stationary.asc", overwrite = T)
writeRaster(q93_stationary, "maps/q93_stationary.asc", overwrite = T)

```

