---
title: "sspf_plots"
author: "anne"
date: "21 januar 2020"
output: word_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## change memory size  
Maybe it is necessary to extend the memory limit, because the models are quite large.
This is how it is done. It re-sets itself when the R-session is terminated.
```{r}
# To check the current memory limit
memory.limit() #[1] 8062 -----> default
# To check the current size (only when not changed) and to change the memory limit
memory.size(30000) # Put the new memory size into the bracktes, e.g. 9000
```
  

## Load the model
```{r}
load("output/sspf/mod_sspf_allyear.rda")
load("processdata/sspf/dat.rda")
# dat <- dat_red
library(ResourceSelection)

summary(mod_sspf_allyear)

```


## create dataframe for a model or several models
```{r}
mod_sspf_allyear_rspfframe <- data.frame(Variable = rownames(summary(mod_sspf_allyear)$coef),
                            Coefficient = summary(mod_sspf_allyear)$coef[, 1],
                            SE = summary(mod_sspf_allyear)$coef[, 2],
                            modelname = "mod_sspf_allyear")
```


## Combine these data.frames
```{r}
# allmodelframe_rspf <- data.frame(rbind(mod11_99boot_rspfframe, mod11a_99boot_rspfframe, mod11b_99boot_rspfframe, mod11c_99boot_rspfframe))

allmodelframe_sspf <- data.frame(rbind(mod_sspf_allyear_rspfframe))

```

## Confidence interval
```{r}
  interval1 <- -qnorm((1-0.95)/2)  # 95% multiplier
  interval2 <- -qnorm((1-0.95)/2)  # 95% multiplier
```

## Plots
#### Forest plot (estimates), can also be usd to compare models
```{r}
library(ggplot2) 
 ggplot(allmodelframe_sspf, aes(colour = modelname)) + 
    geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) + 
    geom_linerange(aes(x = Variable, ymin = Coefficient - SE*interval1,
                                  ymax = Coefficient + SE*interval1),
                              lwd = 1, position = position_dodge(width = 1/2)) + 
    geom_pointrange(aes(x = Variable, y = Coefficient, ymin = Coefficient - SE*interval2,
                                   ymax = Coefficient + SE*interval2),
                               lwd = 1/2, position = position_dodge(width = 1/2),
                               shape = 21, fill = "WHITE") + coord_flip() + theme_bw()+
  ggtitle("")
```

#### Effect plots
```{r}
library(effects)
plot(allEffects(mod_sspf_allyear))
plot(effect("log_road_dist:road_traffic_high", mod_sspf_allyear))
# plot(Effect(c("log_road_dist", "traffic_high"), mod11_rspf_99boot)) # just gives the same as the effect with interaction


# mep(mod11_rspf_99boot)
# kdepairs(mod11_rspf_99boot)

```

#### Use vs. distance to road plots
Plot of selection against road variables.
Change "d" to d2 and "m" to m2 and so on when changing the input model.
```{r}
load("output/mod1_rspf.rda")
load("processdata/datrsf4.rda")
tmp <- datrsf4
          newdat <- tmp[rep(1, 2000),] 
          newdat$road_dist <- c(c(0,0:498)*2, c(0,0:498)*2, c(0,0:498)*2, c(0,0:498)*2) #x axis (0=crossing, then from (0=no crossing) to 996 m in steps of 2 - the whole thing repeated 4 times
          newdat$log_road_dist <- log10(newdat$road_dist+1)  
          hist(datrsf4$road_traffic[datrsf4$road_traffic>0])
          quantile(datrsf4$road_traffic[datrsf4$road_traffic>0], 0.25)
          quantile(datrsf4$road_traffic[datrsf4$road_traffic>0], 0.95)
          newdat$road_traffic <- rep(c(0,0,1500,20000), each=500) # we don't predcit traffic in a continuous way - we use cross; no traffic, low, med and high traffic
          newdat$log_road_traffic <- log10(newdat$road_traffic+1)
          newdat$road_type_public <- 0
          newdat$road_type_public[c(1:500)] <- 1
          newdat$road_type_public <- as.factor(newdat$road_type_public)
          
library("boot", lib.loc="~/R/win-library/3.4")
d3 <- newdat
m3 <- mod3_rspf

#  I think that model.matrix will generate automatically the columns that you need, give it a try:

# d <- na.omit(d)

x3 <- model.matrix(m3$formula, data=d3)
    
coefs <- coef(m3)
names(coefs)[15] <- "log_road_dist:road_type_public1"
coefs
predvals <- (X %*% coefs[match(colnames(X), names(coefs))])[,1]
     
d2$linpred <- predvals
d2$predprob <- inv.logit(d2$linpred)
head(d2)

```


For the model with "road_type" instead of "road_traffic".
```{r}
# load("output/mod3_rspf.rda")
# load("processdata/datrsf4.rda")
tmp <- datrsf8
          newdat <- tmp[rep(1, 500*5),] 
          newdat$road_dist <- rep(c(1:500)*2, 5)
          newdat$log_road_dist <- log10(newdat$road_dist+1)
          newdat$road_type <- rep(levels(datrsf8$road_type), each=500)
          newdat$road_type <- as.factor(newdat$road_type)
          newdat$road_type <- factor(newdat$road_type, levels = c("P", "E", "F", "K", "S"))

library(boot)
d8 <- newdat
m6 <- mod11a_rspf_99boot


# d <- na.omit(d)

x6 <- model.matrix(m6$formula, data=d8)

# coefs <- coef(m5)
# names(coefs)[15] <- "log_road_dist:road_type_public1"
# coefs
# predvals <- (X %*% coefs[match(colnames(X), names(coefs))])[,1]

predvals <- (x6 %*% coef(m6)[match(colnames(x6), names(coef(m6)))])[,1]

d8$linpred <- predvals
d8$predprob <- inv.logit(d8$linpred)
head(d8)

```




```{r}

plot(newdat$road_dist[newdat$road_type=="E"], d8$predprob[newdat$road_type=="E"], type="l", col="red", ylim=c(), xlim = c(),
xlab="Avstand til veg (meter)", ylab="valg", cex.lab=1.5, cex.axis=1.1, lty=1, lwd=2) #
lines(newdat$road_dist[newdat$road_type=="F"], d8$predprob[newdat$road_type=="F"], type="l", col="blue", lty=1.5, lwd=2) #

lines(newdat$road_dist[newdat$road_type=="K"], d8$predprob[newdat$road_type=="K"], type="l", col="grey", lty=1.5, lwd=2)
          
lines(newdat$road_dist[newdat$road_type=="P"], d8$predprob[newdat$road_type=="P"], type="l", col="brown", lty=1.5, lwd=2) 

lines(newdat$road_dist[newdat$road_type=="S"], d8$predprob[newdat$road_type=="S"], type="l", col="green", lty=1.5, lwd=2)

# lines(newdat$road_dist[newdat$road_type=="R"], d8$predprob[newdat$road_type=="R"], type="l", col="yellow", lty=1.5, lwd=2)
 



# points(newdat$road_dist[newdat$road_traffic==0 & newdat$road_type_public==1], d$predprob[newdat$road_traffic==0 & newdat$road_type_public==1], pch=8, col="black") 
#           
# points(newdat$road_dist[newdat$road_traffic==20000 & newdat$road_dist==0], d$predprob[newdat$road_traffic==20000 & newdat$road_dist==0], pch=16, col="red") 
# points(newdat$road_dist[newdat$road_traffic==1500 & newdat$road_dist==0], d$predprob[newdat$road_traffic==1500 & newdat$road_dist==0], pch=16, col="blue") 
# 
# points(newdat$road_dist[newdat$road_traffic==0 & newdat$road_type_public==1  & newdat$road_dist==0], d$predprob[newdat$road_traffic==0 & newdat$road_type_public==1  & newdat$road_dist==0], pch=16, col="black") 

```
