---
title: "11_maps_without_crossings"
author: "anne"
date: "28 januar 2020"
output: word_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## change memory size  
Maybe it is necessary to extend the memory limit, because the models are quite large.
This is how it is done. It re-sets itself when the R-session is terminated.
```{r}
# To check the current memory limit
memory.limit() #[1] 8062 -----> default
# To check the current size (only when not changed) and to change the memory limit
memory.size(30000) # Put the new memory size into the bracktes, e.g. 9000
```

## Load models and packages
```{r}
load("output/sspf/mod_sspf_allyear.rda")

# mod_sspf_allyear <-  rspf_parallel(use~ step_length + I(step_length^2) + prop_young_forest + slope + crossed_rail + log_dist_building + prop_ar5_agri +  prop_ar5_bog + prop_ar5_urban + prop_old_forest + prop_water + road_cross + crossing + dist_passage + log_road_dist + road_traffic_high + log_road_dist:road_traffic_high + road_cross:road_traffic_high, data=dat, inits=ints, m=dat$strat, B=99, cl=10, method= "Nelder-Mead", link="logit")

# summary(mod_sspf_allyear)
# 
# mod_sspf_allyear <- data.frame(Variable = rownames(summary(mod_sspf_allyear)$coef),
#                             Coefficient = summary(mod_sspf_allyear)$coef[, 1],
#                             SE = summary(mod_sspf_allyear)$coef[, 2],
#                             modelname = "mod_sspf_allyear")
# # allmodelframe <- data.frame(rbind(mod_sspf_allyear))
# interval1 <- -qnorm((1-0.95)/2)  # 90% multiplier
# interval2 <- -qnorm((1-0.95)/2)  # 95% multiplier
# ggplot(mod_sspf_allyear, aes(colour = modelname)) + 
#     geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) + 
#     geom_linerange(aes(x = Variable, ymin = Coefficient - SE*interval1,
#                                   ymax = Coefficient + SE*interval1),
#                               lwd = 1, position = position_dodge(width = 1/2)) + 
#     geom_pointrange(aes(x = Variable, y = Coefficient, ymin = Coefficient - SE*interval2,
#                                    ymax = Coefficient + SE*interval2),
#                                lwd = 1/2, position = position_dodge(width = 1/2),
#                                shape = 21, fill = "WHITE") + coord_flip() + theme_bw() + 
#     ggtitle("sspf estimates and CI")


library(ResourceSelection)
library(raster)
library(rgdal)
library(boot)
library(ggplot2)

```

```{r}
library(sp) # maybe sf library
library(sf)
library(maptools)
library(spatialEco)


# SpatialPoints() # loads an existing shape file


## With maptool
# roads <- readShapeLines("maps/Vbase_Public_roads_Gardermoen_clipped")
## With sf
roads <- st_read("maps/Vbase_Public_roads_Gardermoen_clipped.shp")
crs(roads) <- CRS("+proj=utm +zone=33 +datum=WGS84 +units=m +no_defs")
roads <- spTransform(roads, CRS("+proj=utm +zone=32 +datum=WGS84 +units=m +no_defs"))

# random_points <- spsample(roads, n = 21, type = "random", cellsize = 23.3588)
random_points <- sample.line(roads, n = 21, type = "random", longlat = TRUE)
plot(crossings_green)
plot(roads, add=T)
plot(random_points, add=T)

random_points1 <- rasterize(x = random_points, y = crossings_green)
random_points_rast <- random_points1[[1]]
values(random_points_rast) <- ifelse(is.na(values(random_points_rast)), 0, 1)
plot(random_points_rast)
plot(random_points, add=T)


writeRaster(random_points_rast, "maps/random_points_rast.tif", overwrite = T)



sp.lines <- SpatialLines(list(Lines(list(Line(cbind(c(1,2,3),c(3,2,2)))), 
               ID="2")))
 sp.lines <- SpatialLinesDataFrame( sp.lines, data.frame(ID=1:2, 
                                    row.names=c(1,2)) )

# Create fixed size (n = 20) random sample 
 rand.sample <- sample.line(sp.lines, n = 20, type = "random", 
                            longlat = TRUE)  
   plot(sp.lines)
     plot(rand.sample, pch = 20, add = TRUE)
     box()	  
     title("rand n = 20")


```



## Make raster stack 

#### Choose what raster to produce
```{r}
name_raster <- "no_road_barrier"

name_raster <- "no_crossings_full_barrier"

name_raster <- "current"

name_raster <- "no_humans"

name_raster <- "random_points"

```


#### load raster layers
```{r}

dist_building <- raster("maps/dist_building.tif")
dist_roads <- raster("maps/dist_roads.tif")
road_traffic_high <- raster("maps/dist_road_traffic_high.tif")
road_cross <- raster("maps/dist_roads.tif")
dist_passage <- raster("maps/sspf/fence.tif")
prop_young_forest <- raster("maps/sspf/prop_young_forest.tif")
slope <- raster("maps/sspf/slope.tif")
prop_ar5_agri <- raster("maps/sspf/prop_ar5_agri.tif")
prop_ar5_bog <- raster("maps/sspf/prop_ar5_bog.tif")
prop_ar5_urban <- raster("maps/sspf/prop_ar5_urban.tif")
prop_old_forest <- raster("maps/sspf/prop_old_forest.tif")
prop_water <- raster("maps/sspf/prop_water.tif")
rail_cross <- raster("maps/sspf/crossed_rail.tif")
crossings_grey <- raster("maps/sspf/crossings_grey.tif")
crossings_high_use <- raster("maps/sspf/crossings_high_use.tif")
crossings_low_use <- raster("maps/sspf/crossings_low_use.tif")
crossings_green <- raster("maps/sspf/crossings_green.tif")


if (name_raster=="random_points"){
  crossings_green <- raster("maps/random_points1.tif")
}


if (name_raster=="no_road_barrier"){
values(dist_roads) <- 900 # 900 = quantile 99% road_dist
values(road_traffic_high) <- 0
values(road_cross) <- 0
values(dist_passage) <- 0
}

if (name_raster=="no_crossings_full_barrier"){
values(dist_passage) <- ifelse(values(dist_passage) == 1, 3000, 0) # 3000 = quantile 95% dist_passage
}

if(name_raster!="current" & name_raster!="random_points"){
values(crossings_grey) <- 0
values(crossings_high_use) <- 0
values(crossings_low_use) <- 0
values(crossings_green) <- 0
}


if (name_raster=="no_humans"){
values(dist_roads) <- 900 # 900 = quantile 99% road_dist
values(road_traffic_high) <- 0
values(road_cross) <- 0
values(dist_passage) <- 0
values(prop_ar5_urban) <- 0
# values(prop_ar5_agri) <- 0
values(dist_building) <- 0
}



```




#### aggregate the layers to resolution I want to use 
```{r}
## Example
# newLayer <- aggregate(currentLayer, fact = 4, fun = mean) # 4 (93m), 3 (70m) = for stationary, 6 for migratory, fun can be: mean, modal, min or max

## permeability
prop_young_forest <- aggregate(prop_young_forest, fact = 4, fun = mean)
slope <- aggregate(slope, fact = 4, fun = mean)
rail_cross <- aggregate(rail_cross, fact = 4, fun = max)
dist_building <- aggregate(dist_building, fact = 4, fun = mean)
prop_ar5_agri <- aggregate(prop_ar5_agri, fact = 4, fun = mean)
prop_ar5_bog <- aggregate(prop_ar5_bog, fact = 4, fun = mean)
prop_ar5_urban <- aggregate(prop_ar5_urban, fact = 4, fun = mean)
prop_old_forest <- aggregate(prop_old_forest, fact = 4, fun = mean)
prop_water <- aggregate(prop_water, fact = 4, fun = mean)
road_cross <- aggregate(road_cross, fact = 4, fun = max)
crossings_grey <- aggregate(crossings_grey, fact = 4, fun = max)
crossings_high_use <- aggregate(crossings_high_use, fact = 4, fun = max)
crossings_low_use <- aggregate(crossings_low_use, fact = 4, fun = max)
crossings_green <- aggregate(crossings_green, fact = 4, fun = max)
dist_passage <- aggregate(dist_passage, fact = 4, fun = min)
dist_roads <- aggregate(dist_roads, fact = 4, fun = min)
road_traffic_high <- aggregate(road_traffic_high, fact = 4, fun = max)
random_points <- aggregate(random_points, fact = 4, fun = max)
# interaction1 <- aggregate(interaction1, fact = 5, fun = mean)
# interaction2 <- aggregate(interaction2, fact = 5, fun = mean)



```


#### Transform layers 
```{r}

log_dist_building <- dist_building
values(log_dist_building) <- log10(values(log_dist_building) + 1)

log_road_dist <- dist_roads
values(log_road_dist) <- log10(values(log_road_dist)+1)

interaction1 <- interaction2 <- road_traffic_high


values(road_cross) <- ifelse(values(road_cross)==0, 1, 0)


if (name_raster!="current"){
values(road_cross) <- 0
}


if (name_raster=="current"){
values(dist_passage) <- ifelse(values(dist_passage)==0, 0, 800) #at 800 any effect of the passage seems to be gone
values(dist_passage) <- ifelse(values(crossings_grey)==1, 0, values(dist_passage))
values(dist_passage) <- ifelse(values(crossings_high_use)==1, 0, values(dist_passage))
values(dist_passage) <- ifelse(values(crossings_low_use)==1, 0, values(dist_passage))
values(dist_passage) <- ifelse(values(crossings_green)==1, 0, values(dist_passage))
}


if (name_raster!="no_road_barrier" & name_raster!="no_humans"){
values(road_traffic_high) <- ifelse(values(dist_roads) < values(road_traffic_high),0,1)
}


if (name_raster!="no_road_barrier" & name_raster!="no_humans"){
values(interaction1) <- values(log_road_dist)*values(road_traffic_high)
values(interaction2) <- values(road_cross)*values(road_traffic_high)
}


```




## Make brick --> ! needs to be in the same order as model variables in model !
```{r}

## permeability
mybrick <- prop_young_forest
mybrick <- brick(mybrick)
mybrick <- addLayer(mybrick, slope)
mybrick <- addLayer(mybrick, rail_cross)
mybrick <- addLayer(mybrick, log_dist_building)
mybrick <- addLayer(mybrick, prop_ar5_agri)
mybrick <- addLayer(mybrick, prop_ar5_bog)
mybrick <- addLayer(mybrick, prop_ar5_urban)
mybrick <- addLayer(mybrick, prop_old_forest)
mybrick <- addLayer(mybrick, prop_water)
mybrick <- addLayer(mybrick, road_cross)
mybrick <- addLayer(mybrick, crossings_grey)
mybrick <- addLayer(mybrick, crossings_high_use)
mybrick <- addLayer(mybrick, crossings_low_use)
mybrick <- addLayer(mybrick, crossings_green)
mybrick <- addLayer(mybrick, dist_passage)
mybrick <- addLayer(mybrick, log_road_dist)
mybrick <- addLayer(mybrick, road_traffic_high)
mybrick <- addLayer(mybrick, interaction1, interaction2)

mybrick <- addLayer(mybrick, random_points)

```



## Predict

#### Load model
```{r}

rspf_mod <- mod_sspf_allyear
coefs <- rspf_mod$coefficients

```

#### Make newdat
```{r}

## permeability --------------------
newdat <- as.data.frame(mybrick)
str(newdat)
# newdat[,3] <- as.numeric(newdat[,3])
# table(newdat[,3])
# newdat[,3] <- ifelse(newdat[,3]==1, 0, 1)
# str(newdat)

tmp <- newdat[,15]
sum(is.na(tmp)) #I don't get it, but it seems to correspond with the values of 800
# newdat[,15] <- as.numeric(newdat[,15])
# newdat[,15] <- ifelse(is.na(tmp), 800, 0)
# table(newdat[,15])
# str(newdat)

newdat <- data.frame(intercept = 1, step_length = 93.43521, squareLS = 93.43521^2, newdat)
newdat <- as.matrix(newdat)
head(newdat)

```

#### Predict
```{r}
predvals <- (newdat %*% coefs)

linpred <- predvals[,1]
predprob <- inv.logit(linpred)

```

#### Make new raster map
```{r}
permeability_no_humans <- prop_young_forest # just use any layer
values(permeability_no_humans) <- predprob

plot(permeability_no_humans)
str(permeability_no_humans)
res(permeability_no_humans)


writeRaster(permeability_no_humans, "maps/permeability_no_humans.tif", overwrite = T)




# Raster the other maps (quality and permeability)
permeability8_with <- raster("maps/permeability8_with.tif") # current situation
permeability_current <- raster("maps/permeability_current.tif") # current situation
permeability8_without <- raster("maps/permeability8_without.tif")
permeability8_without_all <- raster("maps/permeability8_without_all.tif") # all means all crossings
# permeability8_without_fence <- raster("maps/permeability8_without_fence.tif")
permeability8_without_buildings <- raster("maps/permeability8_without_buildings.tif")
permeability8_without_roads <- raster("maps/permeability8_without_roads.tif")
permeability8_without_roads_and_crossings <- raster("maps/permeability8_without_roads_and_crossings.tif")
permeability8_without_humans <- raster("maps/permeability8_without_humans.tif")

quality6_0804 <- raster("maps/quality6_0804.tif") # current situation
quality6_without_humans_0806 <- raster("maps/quality6_without_humans_0806.tif")
quality6_without_roads_0806 <- raster("maps/quality6_without_roads_0806.tif")

 
```



## Draw extent and crop all maps
```{r}
# rast <- stack(raster(q_name), raster(f_name))
rast <- stack(quality6_0804, permeability_current, permeability_no_humans)

ext <- extent(601484, 632825, 6667439, 6703616)
rast <- crop(rast, ext)
rast
plot(rast)

#### Not sure if I run this...
rast <- aggregate(rast, fact=round(resol/xres(rast))) # Don't know what resol and xres are, or rather which values they should represent - resolution? 
rast

#some plots for checking
plot(rast)
plot(rast[[1]])
plot(rast[[2]])
plot(rast[[3]])
plot(extent(rast), add = T) # Don't know what the add = TRUE does...
rast

```


## Write raster
```{r}
writeRaster(rast[[1]], file="maps/quality_crop_1905.asc", overwrite = F)
writeRaster(rast[[2]], file="maps/permeability_with_crop_1905.asc", overwrite = F)

writeRaster(rast[[3]], file="maps/permeability_current_crop_0810.asc", overwrite = F)
writeRaster(rast[[3]], file="maps/permeability_no_barrierTEST_crop_0910.asc", overwrite = F)
writeRaster(rast[[3]], file="maps/permeability_full_barrier_crop_0810.asc", overwrite = F)
writeRaster(rast[[3]], file="maps/permeability_no_humans_crop_1210.asc", overwrite = T)

```






## (OLD!!!) draw extent (OLD!!!)
```{r}
# Use this...
# q93_stationary <- raster("maps/q93_stationary.asc")
crop_quality5_stationary <- raster("maps/crop_quality5_stationary.asc")
# crop_quality4_migratory <- raster("maps/crop_quality4_migratory.asc")
crop_quality5_stationary_NEW2 <- raster("maps/crop_quality5_stationary_NEW2.asc")
quality_stationary_test3 <- raster("maps/quality_stationary_test3.asc")

# ... or this to crop

# plot(permeability3)
e <- drawExtent()

permeability7_with_1704 <- crop(permeability7_with_1704, crop_quality5_stationary_NEW2)

# p_crop_permeability2 <- crop(permeability2, e)

plot(p_stationary_with_cross_1704)
str(p_stationary_with_cross_0804)
res(p_stationary_with_cross_0804)

e <- p_stationary_with_cross_2802

quality_stationary_test4 <- crop(quality_stationary_test3, e)

p_stationary_with_cross_2802_2 <- crop(p_stationary_with_cross_2802, p_stationary_without_cross_2802)



writeRaster(permeability7_without_1704, "maps/permeability7_without_1704.asc", overwrite = F)

p_stationary_with_cross_2802 <- raster("maps/p_stationary_with_cross_2802.asc")

```



