---
title: "11_maps_without_crossings"
author: "anne"
date: "28 januar 2020"
output: word_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## change memory size  
Maybe it is necessary to extend the memory limit, because the models are quite large.
This is how it is done. It re-sets itself when the R-session is terminated.
```{r}
# To check the current memory limit
memory.limit() #[1] 8062 -----> default
# To check the current size (only when not changed) and to change the memory limit
memory.size(20000) # Put the new memory size into the bracktes, e.g. 9000
```

## Load models and packages
```{r}
load("output/sspf/mod_sspf_allyear.rda")

# mod_sspf_allyear <-  rspf_parallel(use~ step_length + I(step_length^2) + prop_young_forest + slope + crossed_rail + log_dist_building + prop_ar5_agri +  prop_ar5_bog + prop_ar5_urban + prop_old_forest + prop_water + road_cross + crossing + dist_passage + log_road_dist + road_traffic_high + log_road_dist:road_traffic_high + road_cross:road_traffic_high, data=dat, inits=ints, m=dat$strat, B=99, cl=10, method= "Nelder-Mead", link="logit")

# summary(mod_sspf_allyear)
# 
# mod_sspf_allyear <- data.frame(Variable = rownames(summary(mod_sspf_allyear)$coef),
#                             Coefficient = summary(mod_sspf_allyear)$coef[, 1],
#                             SE = summary(mod_sspf_allyear)$coef[, 2],
#                             modelname = "mod_sspf_allyear")
# # allmodelframe <- data.frame(rbind(mod_sspf_allyear))
# interval1 <- -qnorm((1-0.95)/2)  # 90% multiplier
# interval2 <- -qnorm((1-0.95)/2)  # 95% multiplier
# ggplot(mod_sspf_allyear, aes(colour = modelname)) + 
#     geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) + 
#     geom_linerange(aes(x = Variable, ymin = Coefficient - SE*interval1,
#                                   ymax = Coefficient + SE*interval1),
#                               lwd = 1, position = position_dodge(width = 1/2)) + 
#     geom_pointrange(aes(x = Variable, y = Coefficient, ymin = Coefficient - SE*interval2,
#                                    ymax = Coefficient + SE*interval2),
#                                lwd = 1/2, position = position_dodge(width = 1/2),
#                                shape = 21, fill = "WHITE") + coord_flip() + theme_bw() + 
#     ggtitle("sspf estimates and CI")


library(ResourceSelection)
library(raster)
library(rgdal)
library(boot)
library(ggplot2)

```






## To produce random points layers
```{r}
library(sf)
library(spatialEco)
library(tidyverse)
library(stars)

## Load map layers
roads <- st_read("maps/Vbase_Public_roads_Gardermoen_clipped.shp")
roads <- st_transform(roads, crs = "+proj=utm +zone=32 +datum=WGS84 +units=m +no_defs")

dist_building <- raster("maps/dist_building.tif")
dist_roads <- raster("maps/dist_roads.tif")
road_traffic_high <- raster("maps/dist_road_traffic_high.tif")
road_cross <- raster("maps/dist_roads.tif")
dist_passage <- raster("maps/sspf/fence.tif")
prop_young_forest <- raster("maps/sspf/prop_young_forest.tif")
slope <- raster("maps/sspf/slope.tif")
prop_ar5_agri <- raster("maps/sspf/prop_ar5_agri.tif")
prop_ar5_bog <- raster("maps/sspf/prop_ar5_bog.tif")
prop_ar5_urban <- raster("maps/sspf/prop_ar5_urban.tif")
prop_old_forest <- raster("maps/sspf/prop_old_forest.tif")
prop_water <- raster("maps/sspf/prop_water.tif")
rail_cross <- raster("maps/sspf/crossed_rail.tif")
crossings_grey <- raster("maps/sspf/crossings_grey.tif")
crossings_high_use <- raster("maps/sspf/crossings_high_use.tif")
crossings_low_use <- raster("maps/sspf/crossings_low_use.tif")
# crossings_green <- raster("maps/sspf/crossings_green.tif")


## Aggregate map layers
prop_young_forest <- aggregate(prop_young_forest, fact = 4, fun = mean)
slope <- aggregate(slope, fact = 4, fun = mean)
rail_cross <- aggregate(rail_cross, fact = 4, fun = max)
dist_building <- aggregate(dist_building, fact = 4, fun = mean)
prop_ar5_agri <- aggregate(prop_ar5_agri, fact = 4, fun = mean)
prop_ar5_bog <- aggregate(prop_ar5_bog, fact = 4, fun = mean)
prop_ar5_urban <- aggregate(prop_ar5_urban, fact = 4, fun = mean)
prop_old_forest <- aggregate(prop_old_forest, fact = 4, fun = mean)
prop_water <- aggregate(prop_water, fact = 4, fun = mean)
road_cross <- aggregate(road_cross, fact = 4, fun = max)
crossings_grey <- aggregate(crossings_grey, fact = 4, fun = max)
crossings_high_use <- aggregate(crossings_high_use, fact = 4, fun = max)
crossings_low_use <- aggregate(crossings_low_use, fact = 4, fun = max)
dist_passage <- aggregate(dist_passage, fact = 4, fun = min)
dist_roads <- aggregate(dist_roads, fact = 4, fun = min)
road_traffic_high <- aggregate(road_traffic_high, fact = 4, fun = max)

## Transform layers
log_dist_building <- dist_building
values(log_dist_building) <- log10(values(log_dist_building) + 1)
log_road_dist <- dist_roads
values(log_road_dist) <- log10(values(log_road_dist)+1)
interaction1 <- interaction2 <- road_traffic_high
values(road_cross) <- ifelse(values(road_cross)==0, 1, 0)
values(dist_passage) <- ifelse(values(dist_passage)==0, 0, 800) #at 800 any effect of the passage seems to be gone 
values(dist_passage) <- ifelse(values(crossings_grey)==1, 0, values(dist_passage))
values(dist_passage) <- ifelse(values(crossings_high_use)==1, 0, values(dist_passage))
values(dist_passage) <- ifelse(values(crossings_low_use)==1, 0, values(dist_passage))
values(road_traffic_high) <- ifelse(values(dist_roads) < values(road_traffic_high),0,1)
values(interaction1) <- values(log_road_dist)*values(road_traffic_high)
values(interaction2) <- values(road_cross)*values(road_traffic_high)


## Extent
ext <- extent(601484, 632825, 6667439, 6703616)
prop_young_forest <- crop(prop_young_forest, ext)
slope <- crop(slope, ext)
rail_cross <- crop(rail_cross, ext)
log_dist_building <- crop(log_dist_building, ext)
prop_ar5_agri <- crop(prop_ar5_agri, ext)
prop_ar5_bog <- crop(prop_ar5_bog, ext)
prop_ar5_urban <- crop(prop_ar5_urban, ext)
prop_old_forest <- crop(prop_old_forest, ext)
prop_water <- crop(prop_water, ext)
road_cross <- crop(road_cross, ext)
crossings_grey <- crop(crossings_grey, ext)
crossings_high_use <- crop(crossings_high_use, ext)
crossings_low_use <- crop(crossings_low_use, ext)
dist_passage <- crop(dist_passage, ext)
log_road_dist <- crop(log_road_dist, ext)
road_traffic_high <- crop(road_traffic_high, ext)
interaction1 <- crop(interaction1, ext)
interaction2 <- crop(interaction2, ext)

crossings_high_use_stars <- st_as_stars(crossings_high_use)


## Load model
rspf_mod <- mod_sspf_allyear
coefs <- rspf_mod$coefficients


# i=1 # to test your loop
for (i in c(1:100)){
  tmp <- st_line_sample(roads, n = 2, density = 1/200, type = "random") %>%
  st_as_sf() 
  random_points2 <-  st_cast(tmp, 'POINT') %>% 
  sample_n(., 21) %>% # maybe change to 20, to get 21 points in the end
  mutate(points = 1) %>% 
  dplyr::select(points)
  grid <- st_make_grid(random_points2, cellsize = 93.43521) %>%  # maybe change back to 23.3588
  st_as_sf() %>% 
  mutate(id = 1:nrow(.))
  int <- st_intersection(random_points2, grid) %>% st_drop_geometry()
  grid_int <- full_join(int, grid, by = 'id') %>% 
  replace_na(list(points = 0)) %>% 
  st_as_sf()
  bbox <- st_bbox(grid) %>% st_as_stars
  random_points_r <- st_rasterize(grid_int, bbox)
  random_points_r <- st_rasterize(grid_int, crossings_high_use_stars)

  crossings_green <- random_points_r
  crossings_green <- as(crossings_green, "Raster")
  # crossings_green <- aggregate(crossings_green, fact = 4, fun = max) # maybe delete
  values(dist_passage) <- ifelse(values(crossings_green) == 1, 0, values(dist_passage))
  
  mybrick <- prop_young_forest
  mybrick <- brick(mybrick)
  mybrick <- addLayer(mybrick, slope)
  mybrick <- addLayer(mybrick, rail_cross)
  mybrick <- addLayer(mybrick, log_dist_building)
  mybrick <- addLayer(mybrick, prop_ar5_agri)
  mybrick <- addLayer(mybrick, prop_ar5_bog)
  mybrick <- addLayer(mybrick, prop_ar5_urban)
  mybrick <- addLayer(mybrick, prop_old_forest)
  mybrick <- addLayer(mybrick, prop_water)
  mybrick <- addLayer(mybrick, road_cross)
  mybrick <- addLayer(mybrick, crossings_grey)
  mybrick <- addLayer(mybrick, crossings_high_use)
  mybrick <- addLayer(mybrick, crossings_low_use)
  mybrick <- addLayer(mybrick, crossings_green)
  mybrick <- addLayer(mybrick, dist_passage)
  mybrick <- addLayer(mybrick, log_road_dist)
  mybrick <- addLayer(mybrick, road_traffic_high)
  mybrick <- addLayer(mybrick, interaction1, interaction2)
  newdat <- as.data.frame(mybrick)
  newdat <- data.frame(intercept = 1, step_length = 93.43521, squareLS = 93.43521^2, newdat)
  newdat <- as.matrix(newdat)
  predvals <- (newdat %*% coefs)
  linpred <- predvals[,1]
  predprob <- inv.logit(linpred)
  permeability_random_points <- prop_young_forest # just use any layer
  values(permeability_random_points) <- predprob

  writeRaster(permeability_random_points, file=paste0("maps/rep_random_points/permeability_random_points",i,".asc"), overwrite=T)
}


# permeability_random_points1 <- raster("maps/rep_random_points/permeability_random_points1.asc")
# plot(permeability_random_points1)


```





## Make raster stack 

#### Choose what raster to produce
```{r}
name_raster <- "no_road_barrier"

name_raster <- "no_crossings_full_barrier"

name_raster <- "current"

name_raster <- "no_humans"


```


#### load raster layers
```{r}
library(raster)


dist_building <- raster("maps/dist_building.tif")
dist_roads <- raster("maps/dist_roads.tif")
road_traffic_high <- raster("maps/dist_road_traffic_high.tif")
road_cross <- raster("maps/dist_roads.tif")
dist_passage <- raster("maps/sspf/fence.tif")
prop_young_forest <- raster("maps/sspf/prop_young_forest.tif")
slope <- raster("maps/sspf/slope.tif")
prop_ar5_agri <- raster("maps/sspf/prop_ar5_agri.tif")
prop_ar5_bog <- raster("maps/sspf/prop_ar5_bog.tif")
prop_ar5_urban <- raster("maps/sspf/prop_ar5_urban.tif")
prop_old_forest <- raster("maps/sspf/prop_old_forest.tif")
prop_water <- raster("maps/sspf/prop_water.tif")
rail_cross <- raster("maps/sspf/crossed_rail.tif")
crossings_grey <- raster("maps/sspf/crossings_grey.tif")
crossings_high_use <- raster("maps/sspf/crossings_high_use.tif")
crossings_low_use <- raster("maps/sspf/crossings_low_use.tif")
crossings_green <- raster("maps/sspf/crossings_green.tif")



if (name_raster=="no_road_barrier"){
values(dist_roads) <- 900 # 900 = quantile 99% road_dist
values(road_traffic_high) <- 0
values(road_cross) <- 0
values(dist_passage) <- 0
}

if (name_raster=="no_crossings_full_barrier"){
values(dist_passage) <- ifelse(values(dist_passage) == 1, 3000, 0) # 3000 = quantile 95% dist_passage
}

if(name_raster!="current"){
values(crossings_grey) <- 0
values(crossings_high_use) <- 0
values(crossings_low_use) <- 0
values(crossings_green) <- 0
}


if (name_raster=="no_humans"){
values(dist_roads) <- 900 # 900 = quantile 99% road_dist
values(road_traffic_high) <- 0
values(road_cross) <- 0
values(dist_passage) <- 0
values(prop_ar5_urban) <- 0
values(prop_ar5_agri) <- 0
values(dist_building) <- 0
}



```




#### aggregate the layers to resolution I want to use 
```{r}
## Example
# newLayer <- aggregate(currentLayer, fact = 4, fun = mean) # 4 (93m), 3 (70m) = for stationary, 6 for migratory, fun can be: mean, modal, min or max

## permeability
prop_young_forest <- aggregate(prop_young_forest, fact = 4, fun = mean)
slope <- aggregate(slope, fact = 4, fun = mean)
rail_cross <- aggregate(rail_cross, fact = 4, fun = max)
dist_building <- aggregate(dist_building, fact = 4, fun = mean)
prop_ar5_agri <- aggregate(prop_ar5_agri, fact = 4, fun = mean)
prop_ar5_bog <- aggregate(prop_ar5_bog, fact = 4, fun = mean)
prop_ar5_urban <- aggregate(prop_ar5_urban, fact = 4, fun = mean)
prop_old_forest <- aggregate(prop_old_forest, fact = 4, fun = mean)
prop_water <- aggregate(prop_water, fact = 4, fun = mean)
road_cross <- aggregate(road_cross, fact = 4, fun = max)
crossings_grey <- aggregate(crossings_grey, fact = 4, fun = max)
crossings_high_use <- aggregate(crossings_high_use, fact = 4, fun = max)
crossings_low_use <- aggregate(crossings_low_use, fact = 4, fun = max)
crossings_green <- aggregate(crossings_green, fact = 4, fun = max)
dist_passage <- aggregate(dist_passage, fact = 4, fun = min)
dist_roads <- aggregate(dist_roads, fact = 4, fun = min)
road_traffic_high <- aggregate(road_traffic_high, fact = 4, fun = max)
# random_points <- aggregate(random_points, fact = 4, fun = max)
# interaction1 <- aggregate(interaction1, fact = 5, fun = mean)
# interaction2 <- aggregate(interaction2, fact = 5, fun = mean)



```


#### Transform layers 
```{r}

log_dist_building <- dist_building
values(log_dist_building) <- log10(values(log_dist_building) + 1)

log_road_dist <- dist_roads
values(log_road_dist) <- log10(values(log_road_dist)+1)

interaction1 <- interaction2 <- road_traffic_high


values(road_cross) <- ifelse(values(road_cross)==0, 1, 0)


if (name_raster!="current"){
values(road_cross) <- 0
}


if (name_raster=="current"){
values(dist_passage) <- ifelse(values(dist_passage)==0, 0, 800) #at 800 any effect of the passage seems to be gone
values(dist_passage) <- ifelse(values(crossings_grey)==1, 0, values(dist_passage))
values(dist_passage) <- ifelse(values(crossings_high_use)==1, 0, values(dist_passage))
values(dist_passage) <- ifelse(values(crossings_low_use)==1, 0, values(dist_passage))
values(dist_passage) <- ifelse(values(crossings_green)==1, 0, values(dist_passage))
}


if (name_raster!="no_road_barrier" & name_raster!="no_humans"){
values(road_traffic_high) <- ifelse(values(dist_roads) < values(road_traffic_high),0,1)
}


if (name_raster!="no_road_barrier" & name_raster!="no_humans"){
values(interaction1) <- values(log_road_dist)*values(road_traffic_high)
values(interaction2) <- values(road_cross)*values(road_traffic_high)
}


```




## Make brick --> ! needs to be in the same order as model variables in model !
```{r}

## permeability
mybrick <- prop_young_forest
mybrick <- brick(mybrick)
mybrick <- addLayer(mybrick, slope)
mybrick <- addLayer(mybrick, rail_cross)
mybrick <- addLayer(mybrick, log_dist_building)
mybrick <- addLayer(mybrick, prop_ar5_agri)
mybrick <- addLayer(mybrick, prop_ar5_bog)
mybrick <- addLayer(mybrick, prop_ar5_urban)
mybrick <- addLayer(mybrick, prop_old_forest)
mybrick <- addLayer(mybrick, prop_water)
mybrick <- addLayer(mybrick, road_cross)
mybrick <- addLayer(mybrick, crossings_grey)
mybrick <- addLayer(mybrick, crossings_high_use)
mybrick <- addLayer(mybrick, crossings_low_use)
mybrick <- addLayer(mybrick, crossings_green)
mybrick <- addLayer(mybrick, dist_passage)
mybrick <- addLayer(mybrick, log_road_dist)
mybrick <- addLayer(mybrick, road_traffic_high)
mybrick <- addLayer(mybrick, interaction1, interaction2)



```



## Predict

#### Load model
```{r}

rspf_mod <- mod_sspf_allyear
coefs <- rspf_mod$coefficients

```

#### Make newdat
```{r}

## permeability --------------------
newdat <- as.data.frame(mybrick)
str(newdat)
# newdat[,3] <- as.numeric(newdat[,3])
# table(newdat[,3])
# newdat[,3] <- ifelse(newdat[,3]==1, 0, 1)
# str(newdat)

tmp <- newdat[,15]
sum(is.na(tmp)) #I don't get it, but it seems to correspond with the values of 800
# newdat[,15] <- as.numeric(newdat[,15])
# newdat[,15] <- ifelse(is.na(tmp), 800, 0)
# table(newdat[,15])
# str(newdat)

newdat <- data.frame(intercept = 1, step_length = 93.43521, squareLS = 93.43521^2, newdat)
newdat <- as.matrix(newdat)
head(newdat)

```

#### Predict
```{r}
predvals <- (newdat %*% coefs)

linpred <- predvals[,1]
predprob <- inv.logit(linpred)

```

#### Make new raster map
```{r}
permeability_without_roads_1501 <- prop_young_forest # just use any layer
values(permeability_without_roads_1501) <- predprob

# plot(permeability_without_humans_1501)
# str(permeability_without_humans_1501)
# res(permeability_without_humans_1501)


# writeRaster(permeability_without_humans_1501, "maps/permeability_without_humans_1501.tif", overwrite = T)


 
```



## Draw extent and crop all maps
```{r}
# Raster the other maps (quality and permeability)
permeability8_with <- raster("maps/permeability8_with.tif") # old current situation 
permeability_current <- raster("maps/permeability_current.tif") # current situation
permeability8_without <- raster("maps/permeability8_without.tif")
permeability8_without_all <- raster("maps/permeability8_without_all.tif") # all means all crossings
# permeability8_without_fence <- raster("maps/permeability8_without_fence.tif")
permeability8_without_buildings <- raster("maps/permeability8_without_buildings.tif")
permeability8_without_roads <- raster("maps/permeability8_without_roads.tif")
permeability8_without_roads_and_crossings <- raster("maps/permeability8_without_roads_and_crossings.tif")
permeability8_without_humans <- raster("maps/permeability8_without_humans.tif")
permeability_random_points <- raster("maps/permeability_random_points.tif")

quality6_0804 <- raster("maps/quality6_0804.tif") # current situation
quality6_without_humans_0806 <- raster("maps/quality6_without_humans_0806.tif")
quality6_without_roads_0806 <- raster("maps/quality6_without_roads_0806.tif")



# rast <- stack(raster(q_name), raster(f_name))
rast <- stack(quality_without_roads_1501, permeability_current)

ext <- extent(601484, 632825, 6667439, 6703616)
rast <- crop(rast, ext)
rast
plot(rast)

## To test julia loop
plot(quality6_0804)
e <- drawExtent()
rast <- crop(rast, e)
plot(rast)
rast

#### Not sure if I run this...
# rast <- aggregate(rast, fact=round(resol/xres(rast))) # Don't know what resol and xres are, or rather which values they should represent - resolution? 
# rast

#some plots for checking
# plot(rast)
# plot(rast[[1]])
# plot(rast[[2]])
# plot(rast[[3]])
# plot(extent(rast), add = T) # Don't know what the add = TRUE does...
# rast

```


## Write raster
```{r}
writeRaster(rast[[1]], file="maps/quality_without_roads_crop_1501.asc", overwrite = F)
writeRaster(rast[[2]], file="maps/permeability_with_crop_1905.asc", overwrite = F)

writeRaster(rast[[3]], file="maps/permeability_current_crop_0810.asc", overwrite = F)
writeRaster(rast[[3]], file="maps/permeability_no_barrierTEST_crop_0910.asc", overwrite = F)
writeRaster(rast[[3]], file="maps/permeability_full_barrier_crop_0810.asc", overwrite = F)
writeRaster(rast[[3]], file="maps/permeability_no_humans_crop_1210.asc", overwrite = F)
writeRaster(rast[[3]], file="maps/permeability_without_humans_crop_1501.asc", overwrite = F)
writeRaster(rast[[3]], file="maps/permeability_without_roads_crop_1501.asc", overwrite = F)
# writeRaster(rast[[3]], file="maps/permeability_random_points_crop_1811.asc", overwrite = F)


```




## sum of functions
```{r}
library(raster)

## Permeabilities and qualities ----
# For both Habitat Functionality and road barrier effect
permeability_current_crop_0810 <- raster("maps/final_permability_and_quality/permeability_current_crop_0810.asc")
cellStats(permeability_current_crop_0810, "sum")

quality_current_crop_1905 <- raster("maps/final_permability_and_quality/quality_current_crop_1905.asc")
cellStats(quality_current_crop_1905, "sum")

permeability_full_barrier_crop_0810 <- raster("maps/final_permability_and_quality/permeability_full_barrier_crop_0810.asc") 
cellStats(permeability_full_barrier_crop_0810, "sum") # both for road barrier effect and Habitat Functionality no WCS


# Habitat functionality
quality_without_humans_crop_1501 <- raster("maps/final_permability_and_quality/quality_without_humans_crop_1501.asc")
cellStats(quality_without_humans_crop_1501, "sum")

quality_without_roads_1501 <- raster("maps/final_permability_and_quality/quality_without_roads_1501.asc")
cellStats(quality_without_roads_1501, "sum")


permeability_hf_without_roads_crop_1501 <- raster("maps/final_permability_and_quality/permeability_hf_without_roads_crop_1501.asc")
cellStats(permeability_hf_without_roads_crop_1501, "sum")

permeability_hf_without_humans_crop_1501 <- raster("maps/final_permability_and_quality/permeability_hf_without_humans_crop_1501.asc")
cellStats(permeability_hf_without_humans_crop_1501, "sum")


# Road barrier effect
permeability_no_barrier_crop_0810 <- raster("maps/final_permability_and_quality/permeability_no_barrier_crop_0810.asc")
cellStats(permeability_no_barrier_crop_0810, "sum")

permeability_no_humans_crop_0910 <- raster("maps/final_permability_and_quality/permeability_no_humans_crop_0910.asc")
cellStats(permeability_no_humans_crop_0910, "sum")





## Function outputs ----
# For both Habitat Functionality and road barrier effect
func_current_1210 <- raster("maps/func_julia_outputs/func_current_1210.asc")
cellStats(func_current_1210, "sum")

func_no_crossings_and_full_barrier_1210 <- raster("maps/func_julia_outputs/func_no_crossings_and_full_barrier_1210.asc")
cellStats(func_no_crossings_and_full_barrier_1210, "sum") # both for road barrier effect and Habitat Functionality no WCS

# func_diff_no_crossings_and_full_barrier_1210 <- raster("maps/func_julia_outputs/func_diff_no_crossings_and_full_barrier_1210.asc")
# cellStats(func_diff_no_crossings_and_full_barrier_1210, "sum") # both for road barrier effect and Habitat Functionality no WCS


# Habitat Functionality
# habitat_func_diff_without_humans_1501 <- raster("maps/func_julia_outputs/habitat_func_diff_without_humans_1501.asc")
# cellStats(habitat_func_diff_without_humans_1501, "sum")
# 
# habitat_func_diff_without_roads_1501 <- raster("maps/func_julia_outputs/habitat_func_diff_without_roads_1501.asc")
# cellStats(habitat_func_diff_without_roads_1501, "sum")


habitat_func_without_roads_1501 <- raster("maps/func_julia_outputs/habitat_functionality/habitat_func_without_roads_1501.asc")
cellStats(habitat_func_without_roads_1501, "sum")

habitat_func_without_humans_1501 <- raster("maps/func_julia_outputs/habitat_functionality/habitat_func_without_humans_1501.asc")
cellStats(habitat_func_without_humans_1501, "sum")


# Road barrier effects
# func_diff_no_barrier_2001 <- raster("maps/func_julia_outputs/road_barrier/func_diff_no_barrier_2001.asc")
# cellStats(func_diff_no_barrier_2001, "sum")
# 
# func_diff_no_humans_1210 <- raster("maps/func_julia_outputs/road_barrier/func_diff_no_humans_1210.asc")
# cellStats(func_diff_no_humans_1210, "sum")


func_no_barrier_2001 <- raster("maps/func_julia_outputs/road_barrier/func_no_barrier_2001.asc")
cellStats(func_no_barrier_2001, "sum")

func_no_humans_1210 <- raster("maps/func_julia_outputs/road_barrier/func_no_humans_1210.asc")
cellStats(func_no_humans_1210, "sum")




## Function outputs random points ----
for (i in 1:10) {
  print(cellStats(raster(paste0("maps/rep_random_points_julia/permeability_random_points",i,".asc")),"sum"))
}

# 41618778
# 41618289
# 41619981
# 41620720
# 41619005
# 41619600
# 41619713
# 41620721
# 41618451
# 41617791

```







## (OLD!!!) draw extent (OLD!!!)
```{r}
# Use this...
# q93_stationary <- raster("maps/q93_stationary.asc")
crop_quality5_stationary <- raster("maps/crop_quality5_stationary.asc")
# crop_quality4_migratory <- raster("maps/crop_quality4_migratory.asc")
crop_quality5_stationary_NEW2 <- raster("maps/crop_quality5_stationary_NEW2.asc")
quality_stationary_test3 <- raster("maps/quality_stationary_test3.asc")

# ... or this to crop

# plot(permeability3)
e <- drawExtent()

permeability7_with_1704 <- crop(permeability7_with_1704, crop_quality5_stationary_NEW2)

# p_crop_permeability2 <- crop(permeability2, e)

plot(p_stationary_with_cross_1704)
str(p_stationary_with_cross_0804)
res(p_stationary_with_cross_0804)

e <- p_stationary_with_cross_2802

quality_stationary_test4 <- crop(quality_stationary_test3, e)

p_stationary_with_cross_2802_2 <- crop(p_stationary_with_cross_2802, p_stationary_without_cross_2802)



writeRaster(permeability7_without_1704, "maps/permeability7_without_1704.asc", overwrite = F)

p_stationary_with_cross_2802 <- raster("maps/p_stationary_with_cross_2802.asc")

```



