<<<<<<< HEAD
---
title: "Help"
author: "anneMehl"
date: "10 april 2018"
output: word_document
---

It is also possible to use sth like this:
##### Load package and set knitr root.dir to the right folder
```{r setup, include=FALSE}
require("knitr")
knitr::opts_chunk$set(echo = TRUE)
opts_knit$set(root.dir = "~/vei-veggi-vilt/Paper_1/Analysis/vvvp1")
```

Instead of this:
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

setwd("C:/Users/anne.mehlhoop/OneDrive - NINA/vei-veggi-vilt/Paper_2_connectivity/Analysis/vvvp1")

If there is a problem with the working directory.



#### FOR mixed models which fail to converge
* look in help -> optimize[G]lmer



=======
---
title: "Help"
author: "anneMehl"
date: "10 april 2018"
output: word_document
---

It is also possible to use sth like this:
##### Load package and set knitr root.dir to the right folder
```{r setup, include=FALSE}
require("knitr")
knitr::opts_chunk$set(echo = TRUE)
opts_knit$set(root.dir = "~/vei-veggi-vilt/Paper_1/Analysis/vvvp1")
```

Instead of this:
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

setwd("C:/Users/anne.mehlhoop/OneDrive - NINA/vei-veggi-vilt/Paper_2_connectivity/Analysis/vvvp1")

If there is a problem with the working directory.



#### FOR mixed models which fail to converge
* look in help -> optimize[G]lmer



>>>>>>> 33073c58e577f151a44cf063f78edd1b3c2e3689
